---
title: "Digital literacy reduces susceptibility to populist content on social media"
subtitle: Replication data and code
author: Kristina Aleksandrovna Pedersen, Ferdinand Geissler, Felix Hartmann, Johannes Giesecke, Macartan Humphreys, Heike Klüver
format:
  html:
    number-sections: true
    embed-resources: true
    code-fold: true
    toc: true
execute:
  echo: true
  warning: true
  message: false
---


# Setup

```{r}
#| label: analysis-setup-packages

# Load packages
pacman::p_load(
  forcats,
  scales,
  fixest,
  tidyverse,
  DeclareDesign,
  haven,
  knitr,
  broom,
  ggh4x,
  ellipse,
  ggrepel,
  texreg,
  ggalluvial,
  scales
)

```


## Configuration

```{r}
#| label: analysis-configuration

setFixest_notes(FALSE)  # Suppress fixest NOTE messages
filter_10 <- TRUE
pref_var <- "party_preference_"

# Edit figure labels here
strategies <- 
  c("political\n(emotional)", "political\n(neutral)")

# Unified output directories
fig_dir <- "figs"

# Filename suffix by wave
wave_suffix <- c(
  wave_9 = "_shortterm",
  wave_10 = "_longterm"
)

# Outcomes and groups
v_outcomes <- c(
  "Like" = "videoLikep1r",
  "Share" = "videoSharep1r",
  "Bookmark" = "videoBookmarkp1r",
  "Report" = "videoCommentTickedp1r",
  "Watch Time" = "watch_percentage_",
  "Skip" = "skipped_video_"
)

l_outcomegroups <- list(
  main = c("Like", "Report", "Share", "Bookmark"),
  "_other" = c("Skip", "Watch Time")
)

l_partisanship <- list(
  "Supporter: Yes" = 1,
  "Supporter: No" = 0,
  "All" = c(0, 1)
)

party_codes <-  c("afd", "cdu", "linke", "spd", "gruene", "fdp", "bsw")
party_names <- c("AfD", "CDU/CSU", "Linke",   "SPD",  "Grüne",  "FDP",  "BSW")
names(party_codes) <- party_names
names(party_names) <- party_codes

```


## Helper functions

```{r}
#| label: analysis-helper-functions
# Plot helpers

gg_coefplot <- function(data, aes) {
  ggplot(data, aes) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_point() +
    geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
    theme_tiktok() +
    scale_color_tiktok()
}

# Theme and palette

theme_tiktok <- function() {
  theme_bw() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
    )
}

scale_color_tiktok <- function() {
  scale_color_discrete()
}


# Party identification transition helpers
build_pid_lodes <- function(df_input) {
  labs <- party_names

  from <- df_input |>
    select(id_w9, starts_with("party_id_w9")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      from_party = recode(
        sub("^party_id_w9_(.*)$", "\\1", var),
        !!!labs
      )
    )

  to <- df_input |>
    select(id_w9, starts_with("party_id_w10")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      to_party = recode(
        sub("^party_id_w10_(.*)$", "\\1", var),
        !!!labs
      )
    )

  transitions_indiv <- inner_join(from, to, by = "id_w9")

  transitions <- transitions_indiv |>
    count(`Wave 9` = from_party, `Wave 10` = to_party, name = "Freq")

  totN <- sum(transitions$Freq)

  share_w9 <- transitions |>
    group_by(`Wave 9`) |>
    summarise(s9 = sum(Freq) / totN, .groups = "drop")

  share_w10 <- transitions |>
    group_by(`Wave 10`) |>
    summarise(s10 = sum(Freq) / totN, .groups = "drop")

  net_pp <- share_w10 |>
    left_join(share_w9, by = c("Wave 10" = "Wave 9")) |>
    mutate(
      delta_pp = (s10 - s9) * 100,
      label_right = sprintf("%s\n(%+0.2f pp)", `Wave 10`, delta_pp)
    ) |>
    select(`Wave 10`, label_right)

  lodes <- transitions |>
    mutate(Share = Freq / totN) |>
    to_lodes_form(axes = 1:2, id = "alluvium") |>
    mutate(
      x = factor(x, levels = c("Wave 9", "Wave 10")),
      stratum_lab = ifelse(
        x == "Wave 10",
        net_pp$label_right[match(stratum, net_pp$`Wave 10`)],
        as.character(stratum)
      )
    )

  party_cols <- c(
    "CDU/CSU" = "#000000",
    "SPD" = "#E3000F",
    "Grüne" = "#0DB02B",
    "FDP" = "#FFED00",
    "Linke" = "#E2382A",
    "AfD" = "#009EE0",
    "BSW" = "#18A19A"
  )

  list(lodes = lodes, party_cols = party_cols)
}

plot_pid_alluvial <- function(lodes, party_cols, title_text) {
  ggplot(
    lodes,
    aes(
      x = x,
      stratum = stratum,
      alluvium = alluvium,
      y = Share,
      fill = stratum,
      label = stratum_lab
    )
  ) +
    geom_alluvium(alpha = 0.7, color = NA, knot.pos = 0.4) +
    geom_stratum(fill = "white", color = "black", size = 0.3) +
    geom_text(stat = "stratum", size = 4) +
    scale_fill_manual(values = party_cols, guide = "none") +
    scale_x_discrete(
      labels = c("Wave 9", "Wave 10"),
      expand = c(0.05, 0.05)
    ) +
    labs(
      x = NULL,
      y = NULL,
      title = title_text
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      panel.grid = element_blank(),
      axis.text.y = element_blank()
    )
}

# Build correlation data for a single wave and treatment status
build_cor_df <- function(df, wave_label) {
  groups <- list(
    list(treat = "Treated", data = df |> filter(workshop_Treatment == 1)),
    list(treat = "Control", data = df |> filter(workshop_Treatment == 0))
  )
  purrr::map_df(groups, function(x) {
    df_sel <- x$data |> select(all_of(v_outcomes))
    colnames(df_sel) <- names(v_outcomes)
    cmat <- cor(df_sel, use = "pairwise.complete.obs")
    as.data.frame(as.table(cmat)) |>
      rename(var1 = Var1, var2 = Var2, r = Freq) |>
      mutate(treat = x$treat, wave = wave_label)
  })
}


# Main anlaysis function clusters by ID and fixed effects by video
# Run feols by group and return tidied coefficients with metadata
run_feols_tidy <- function(df, outcome_var, extra_cols = list()) {
  feols(
    as.formula(paste(outcome_var, "~ workshop_Treatment | video")),
    data = df,
    cluster = ~ID
  ) |>
    tidy(conf.int = TRUE) |>
    mutate(!!!extra_cols)
}
```


# Data 

```{r}
#| label: data-imports

datasets <- list(
  wave_9  = read_rds("data/wave_9.rds"),
  wave_10 = read_rds("data/wave_10.rds"))

df_w9_w10  <- read_rds("data/df_w9_w10.rds")|>
  mutate(citysize = as.numeric(citysize))

comments_df <-read.csv("data/comment_classification.csv")

# covariates

# ---- English labels for covariates (matches your df after tolower) ----
labels_en <- c(
  # basics
  alter = "Age",
  geschlecht = "Gender",
  citysize = "City size",

  # region binaries & state dummies
  east = "East (vs West)",
  state_baden_wuerttemberg = "State: Baden-Württemberg",
  state_bayern              = "State: Bavaria",
  state_berlin              = "State: Berlin",
  state_brandenburg         = "State: Brandenburg",
  state_bremen              = "State: Bremen",
  state_hamburg             = "State: Hamburg",
  state_hessen              = "State: Hesse",
  state_mecklenburg_vorpommern = "State: Mecklenburg–Western Pomerania",
  state_niedersachsen          = "State: Lower Saxony",
  state_nordrhein_westfalen    = "State: North Rhine–Westphalia",
  state_rheinland_pfalz        = "State: Rhineland–Palatinate",
  state_saarland               = "State: Saarland",
  state_sachsen                = "State: Saxony",
  state_sachsen_anhalt         = "State: Saxony-Anhalt",
  state_schleswig_holstein     = "State: Schleswig-Holstein",
  state_thueringen             = "State: Thuringia",

  # urbanization binaries
  urban_ballungsraum   = "Urban: Ballungsraum",
  urban_stadtregion    = "Urban: Stadtregion",
  urban_mittelzentrum  = "Urban: Mittelzentrengebiet",
  urban_high           = "Urban (1–2) vs Mittelzentrum (3)",

  # social media (post-lowercase names)
  video_userfacebook       = "Uses Facebook (video)",
  video_usertiktok         = "Uses TikTok (video)",
  video_usersnapchat       = "Uses Snapchat (video)",
  video_userpinterest      = "Uses Pinterest (video)",
  video_userx_ehem_twitter = "Uses X/Twitter (video)",
  video_usertwitch         = "Uses Twitch (video)",

  # attitudes
  politikinteresse = "Political interest",
  competence       = "Perceived competence",
  lr               = "Left–Right ideology",

  # party ID (w9)
  party_id_w9_cdu    = "Party ID: CDU/CSU",
  party_id_w9_spd    = "Party ID: SPD",
  party_id_w9_afd    = "Party ID: AfD",
  party_id_w9_gruene = "Party ID: Greens",
  party_id_w9_fdp    = "Party ID: FDP",
  party_id_w9_linke  = "Party ID: The Left",
  party_id_w9_bsw    = "Party ID: BSW",

  # PTV pre (w9)
  ptv_w9_pre_cdu    = "PTV CDU/CSU (pre)",
  ptv_w9_pre_spd    = "PTV SPD (pre)",
  ptv_w9_pre_linke  = "PTV The Left (pre)",
  ptv_w9_pre_gruene = "PTV Greens (pre)",
  ptv_w9_pre_fdp    = "PTV FDP (pre)",
  ptv_w9_pre_afd    = "PTV AfD (pre)",
  ptv_w9_pre_bsw    = "PTV BSW (pre)",

  # other covariates
  prior_performance_general_2 = "Perceived gov't performance (prior)",
  solidaritat                 = "Solidarity",
  sozialer_zusammenhalt       = "Social cohesion",
  migration                   = "Immigration attitudes",

  # TikTok splits
  tiktok_user_yes       = "Current TikTok user",
  tiktok_user_no        = "Not a TikTok user",
  tiktok_potential_yes  = "Open to get a TikTok account",
  tiktok_potential_no   = "Not open to get a TikTok account",

  # sociodemographics
  beruflicher_status       = "Employment status",
  berufliche_stellung      = "Occupational position",
  bildung_schulisch        = "School education",
  bildung_beruflich        = "Vocational education",
  eigene_kinder            = "Has children",
  haushaltsgrobe           = "Household size",
  migrationshintergrund_eltern = "Parental migration background",
  haushaltseinkommen       = "Household income"
)

```



# Main Results (Figure 1, 4, 5, and associated appendix figures)

Treatment effects by high-level video content types and displays/saves coefficient plots per outcome.

```{r}
#| label: analysis-main-results
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_I <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(unique(df$strategy_2), function(S) {
        df_sub <- df |> filter(strategy_2 == S)
        run_feols_tidy(
          df = df_sub,
          outcome_var = v_outcomes[Y],
          extra_cols = list(outcome = Y, strategy = S)
        )
      }) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_I <- df_f_I |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_I)
    ggsave(
      filename = paste0(
        fig_dir, "/f_I", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_I,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}

```


# Conditional on sender (Figure 2 and related appendix figure)

Treatment effects within each party for political content types, per outcome.

```{r}
#| label: analysis-conditional-on-sender
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIa <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(party_codes), function(P) {
          df_sub <- df |> filter(strategy_2 == S, party == P)
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S, party = P)
          )
        }) |>
          bind_rows()
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIa <- df_f_IIa |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(party)) +
      labs(title = wave_label)

    print(gg_f_IIa)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIa", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIa,
      width = 7,
      height = 6,
      device = cairo_pdf
    )
  }
}
```


# By partisanship (Figure 3 and related appendix figures)

This section estimates treatment effects by partisanship grouping (supporter yes/no/all) within political content types, per outcome.

```{r}
#| label: analysis-by-partisanship
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS) {
          df_sub <- df |>
            filter(strategy_2 == S, partisan %in% l_partisanship[[PS]])
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S, partisan = PS)
          )
        }) |>
          bind_rows()
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc <- df_f_IIc |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(partisan)) +
      labs(title = wave_label)

    print(gg_f_IIc)
    ggsave(filename = paste0(fig_dir, "/f_IIc", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"), 
           plot = gg_f_IIc, width = 7, height = 6, 
           device = cairo_pdf)
  }
}
```




# Other appendix items

## A Descriptives

## C Coding of TikTok videos

## G Engagement with platform

## H Further analysis

### By strategy

This section estimates treatment effects by specific emotional strategies (anger, fear, superiority), per outcome.

* saved as f_IIb files 

```{r}
#| label: analysis-by-strategy
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIb <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(c("anger", "fear", "superiority"), function(S)
        {
          df_sub <- df |> filter(strategy == S)
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S)
          )
        }
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIb <- df_f_IIb |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_IIb)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIb", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIb,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}
```


### f_IIc3: by partisanship and party

This section estimates treatment effects by party and partisanship, with nested facet labels.

```{r}
#| label: analysis-f_IIc3-partisanship-party
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3 <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS)
          lapply(names(party_codes), function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " 
                          (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            run_feols_tidy(
              df = df_temp,
              outcome_var = v_outcomes[Y],
              extra_cols = list(
                outcome = Y,
                strategy = S,
                partisan = as.character(PS),
                party = P
              )
            )
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3 <- df_f_IIc3 |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none",
        axis.text = element_text(size = 6.5)
      )

    print(gg_f_IIc3)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3,
      width = 7,
      height = 11,
      device = cairo_pdf
    )
  }
}
```


###  by partisanship and party (alternate)

suffix: `f_IIc3b`

This alternate visualization repeats f_IIc3 but shows only supporter yes/no levels.

```{r}
#| label: analysis-f_IIc3b-partisanship-party-alt
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3b <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship[1:2]), function(PS)
          lapply(names(party_codes), function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            run_feols_tidy(
              df = df_temp,
              outcome_var = v_outcomes[Y],
              extra_cols = list(
                outcome = Y,
                strategy = S,
                partisan = as.character(PS),
                party = P
              )
            )
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3b <- df_f_IIc3b |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none"
      )

    print(gg_f_IIc3b)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3b", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3b,
      width = 7,
      height = 8,
      device = cairo_pdf
    )
  }
}
```



## Appendix I: Attrition analysis

```{r}
#| label: analysis-attrition
#| message: false
#| warning: false
#| fig-height: 12
#| fig-width: 9


covs <- names(labels_en)
names(covs) <- labels_en


## model 
get_interaction <- function(v) {
  paste0("attrit ~ workshop * ", v) |> 
    as.formula() |>
    lm_robust(data = df_w9_w10 |>
                mutate(across(all_of(v), scale))) |>
    tidy() |>
    filter(grepl(":", term))
}

results <- covs |> lapply(get_interaction) |> bind_rows(.id = "label")

## plot
fig_attrit_interaction <- 
  results |>
  ggplot(aes(x = estimate, y = forcats::fct_reorder(label, estimate))) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0) +
  geom_point() +
  labs(
    title = "Treatment × Covariate Interactions on Attrition (LPM)",
    subtitle = "Points: interaction of treated with covariate; bars: 95% CI",
    x = "Interaction estimate (Δ probability of attrition)",
    y = NULL
  ) +
  theme_bw()

fig_attrit_interaction
  ggsave(filename="figs/fig_attrit_interaction.pdf", plot=fig_attrit_interaction)


```



## Appendix J: Downstream effects on AfD support 


Manual verification of afd voting results:

```{r}
#| label: analysis-maintained-support
#| results: 'asis'

df_w9_w10 <- df_w9_w10 |> 
  mutate(ptv_w9_pre_afd_demeaned = ptv_w9_pre_afd - mean(ptv_w9_pre_afd, na.rm = TRUE),
         party_id_w9_afd_demeaned = party_id_w9_afd - mean(party_id_w9_afd, 
                                            na.rm = TRUE))

by_hand <-
  list(
    identification      = lm_robust(party_id_w10_afd ~ workshop*party_id_w9_afd_demeaned, 
                                    data = df_w9_w10),
    conditional_afd     = lm_robust(party_id_w10_afd ~ workshop, 
                                    data = df_w9_w10 |> filter(party_id_w9_afd == 1)),
    conditional_non_afd = lm_robust(party_id_w10_afd ~ workshop, 
                                    data = df_w9_w10 |> filter(party_id_w9_afd == 0))
  )

# Ensure tabs directory exists and export LaTeX table

texreg::texreg(
  by_hand,
  file      = "tabs/tab_afd_maintained_support.tex",
  digits    = 3,
  include.ci = FALSE,
  custom.model.names = c(
    "All respondents",
    "AfD identifiers",
    "Non-AfD respondents"
  ),
  custom.coef.map = list(
    "(Intercept)"                     = "Intercept",
    "workshop"                        = "Treatment (workshop)",
    "party_id_w9_afd_demeaned"        = "AfD ID (wave 9, demeaned)",
    "workshop:party_id_w9_afd_demeaned" = "Treatment × AfD ID (demeaned)"
  ),
  caption  = "Effect of digital literacy workshop on AfD identification (wave 10).",
  label    = "tab:afd_maintained_support"
)

# Keep HTML version for quick inspection in the rendered document
by_hand |> texreg::htmlreg(digits = 3, include.ci = FALSE)

```

### Additional analysis: conditional effects for all parties

```{r}
#| label: analysis-maintained-support-all-parties
#| fig-height: 7
#| fig-width: 7

# For each party, estimate:
# (a) average effect (interaction model with demeaned ID)
# (b) effect among identifiers
# (c) effect among non-identifiers

maintained_results_raw <-
  party_codes |>
  lapply(function(party) {
    w9  <- paste0("party_id_w9_", party)
    w10 <- paste0("party_id_w10_", party)

    df_tmp <- df_w9_w10 |>
      dplyr::mutate(
        id_w9          = !!rlang::sym(w9),
        id_w9_demeaned = id_w9 - mean(id_w9, na.rm = TRUE),
        id_w10         = !!rlang::sym(w10)
      )

    # (a) Average effect (interaction model with demeaned ID)
    m_all <- lm_robust(id_w10 ~ workshop * id_w9_demeaned, data = df_tmp)

    # (b) Effect among identifiers
    m_id  <- lm_robust(id_w10 ~ workshop,
                       data = df_tmp |> dplyr::filter(id_w9 == 1))

    # (c) Effect among non-identifiers
    m_non <- lm_robust(id_w10 ~ workshop,
                       data = df_tmp |> dplyr::filter(id_w9 == 0))

    dplyr::bind_rows(
      tidy(m_all) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "All respondents"),
      tidy(m_id)  |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Identifiers"),
      tidy(m_non) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Non-identifiers")
    ) |>
      dplyr::mutate(party = party_names[[party]])
  }) |>
  dplyr::bind_rows()

party_order_maintained <-
  maintained_results_raw |>
  dplyr::filter(group == "All respondents") |>
  dplyr::arrange(estimate) |>
  dplyr::pull(party)

maintained_results <-
  maintained_results_raw |>
  dplyr::mutate(
    party = factor(party, levels = party_order_maintained),
    group = factor(
      group,
      levels = c("All respondents", "Identifiers", "Non-identifiers")
    )
  )

fig_maintained_all_parties <-
  maintained_results |>
  ggplot(aes(x = estimate, y = party, color = group)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_point(position = position_dodge(width = 0.6), size = 2.5) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.6),
    height = 0.2
  ) +
  geom_text(
    aes(
      label = sprintf("%.3f (p = %.3f)", estimate, p.value),
      group = group
    ),
    position = position_dodge(width = 0.6),
    hjust = 0.5,
    vjust = -0.7,
    size = 2.5,
    show.legend = FALSE
  ) +
  labs(
    x = "Effect of workshop on party identification (wave 10)",
    y = "Party",
    color = NULL,
    title = "Effects of digital literacy workshop on party identification",
    subtitle = "Average effect, identifiers, and non-identifiers"
  ) +
  theme_bw()

fig_maintained_all_parties

ggsave(
  filename = "figs/fig_maintained_support_all_parties.pdf",
  plot = fig_maintained_all_parties,
  width = 7,
  height = 9,
  device = cairo_pdf
)
```

```{r}
#| label: analysis-party-support-arrows
# Calculate mean party support by treatment group for arrow plot
arrow_data <- df_w9_w10 |> 
  group_by(workshop) |> 
  summarize(
    party_id_w9_afd     = mean(party_id_w9_afd, na.rm = TRUE),
    party_id_w10_afd    = mean(party_id_w10_afd, na.rm = TRUE),
    party_id_w9_cdu     = mean(party_id_w9_cdu, na.rm = TRUE), 
    party_id_w10_cdu    = mean(party_id_w10_cdu, na.rm = TRUE),
    party_id_w9_linke   = mean(party_id_w9_linke, na.rm = TRUE),
    party_id_w10_linke  = mean(party_id_w10_linke, na.rm = TRUE),
    party_id_w9_spd     = mean(party_id_w9_spd, na.rm = TRUE),
    party_id_w10_spd    = mean(party_id_w10_spd, na.rm = TRUE),
    party_id_w9_gruene  = mean(party_id_w9_gruene, na.rm = TRUE),
    party_id_w10_gruene = mean(party_id_w10_gruene, na.rm = TRUE),
    party_id_w9_fdp     = mean(party_id_w9_fdp, na.rm = TRUE),
    party_id_w10_fdp    = mean(party_id_w10_fdp, na.rm = TRUE),
    party_id_w9_bsw     = mean(party_id_w9_bsw, na.rm = TRUE),
    party_id_w10_bsw    = mean(party_id_w10_bsw, na.rm = TRUE)
  ) |> 
  mutate(treatment = ifelse(workshop == 1, "Treatment", "Control"))

# Reshape to long format for plotting
arrow_long <- arrow_data |> 
  pivot_longer(
    cols = starts_with("party_id_w"),
    names_to = c("wave", "party"),
    names_pattern = "party_id_(w\\d+)_(.*)",
    values_to = "support"
  ) |> 
  pivot_wider(names_from = wave, values_from = support) |> 
  mutate(party = case_when(
    party == "afd" ~ "AfD",
    party == "cdu" ~ "CDU/CSU", 
    party == "linke" ~ "Linke",
    party == "spd" ~ "SPD",
    party == "gruene" ~ "Grüne",
    party == "fdp" ~ "FDP",
    party == "bsw" ~ "BSW"
  ))

# Create arrow plot
arrow_segments <- arrow_long |>
  select(treatment, party, w9, w10) |>
  tidyr::pivot_wider(
    names_from = treatment,
    values_from = c(w9, w10),
    names_glue = "{.value}_{treatment}"
  ) |>
  filter(!is.na(w9_Control) & !is.na(w9_Treatment))

p_arrows <- ggplot(arrow_long, aes(x = w9, y = w10)) +
  geom_point(aes(color = treatment), size = 3, alpha = 0.7) +
  geom_segment(
    data = arrow_segments,
    aes(x = w9_Control, y = w10_Control,
        xend = w9_Treatment, yend = w10_Treatment),
    arrow = arrow(length = unit(0.2, "cm")),
    color = "black", size = 1
  ) +
  geom_text_repel(
    aes(label = ifelse(treatment == "Control", party, "")),
    size = 3, force = 2, color = "black"
  ) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    x = "Party Support in Wave 9", 
    y = "Party Support in Wave 10",
    title = "Changes in Party Support: Control vs Treatment",
    subtitle = "Arrows show movement from Control to Treatment group means"
  ) +
  scale_color_manual(values = c("Control" = "#F8766D", "Treatment" = "#00BFC4")) +
  theme_bw() +
  theme(legend.title = element_blank())

print(p_arrows)

ggsave(
  filename = file.path(fig_dir, "party_support_arrows.pdf"),
  plot = p_arrows,
  device = cairo_pdf
)
```


```{r}
#| label: analysis-did-ci-plot


# this model is ANOVA style; w10 conditioning on w9
# not using a change score

over_time_models <-
  party_codes |>
  lapply(function(party) {
    paste0("party_id_w10_", party, " ~ workshop * party_id_w9_", party, "_demean") |>
      as.formula() |>
      lm_robust(data = df_w9_w10) |>
      tidy()
  }) |>
  bind_rows(.id = "party") |>
  filter(term == "workshop")
      
# Create  plot with confidence intervals
plot_change <- function(
    results = over_time_models,
    subtitle = "Effect of treatment on long term support, conditional on initial support") {

  results   |>
  ggplot(aes(x = reorder(party, estimate), y = estimate)) +
  geom_col(aes(fill = ifelse(estimate > 0, "Positive", "Negative")), 
           alpha = 0.7, width = 0.6) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                width = 0.2, color = "black", size = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_text(aes(label = sprintf("%.3f\n(p=%.3f)", estimate, p.value)), 
            size = 2.8) +
  scale_fill_manual(values = c("Positive" = "#2E8B57", "Negative" = "#DC143C")) +
  labs(
    x = "Party",
    y = "Change in support (outcome on 0 to 1 scale)",
    title = "Treatment Effects (with 95% CI)",
    subtitle = subtitle,
    caption = "Error bars show 95% confidence intervals."
  ) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    plot.subtitle = element_text(size = 9),
    plot.caption = element_text(size = 8)
  ) +
  coord_flip()
}

changew9w10 <- plot_change(
  results = over_time_models,
  subtitle = "Effect of treatment on long term support, conditional on initial support")

print(changew9w10)

ggsave(
  filename = file.path(fig_dir, "party_support_did_ci.pdf"),
  plot = changew9w10,
  device = cairo_pdf
)

```


### short term PTV change

```{r}
#| label: analysis-shortterm-plot

# fit PTV_Posterior (wave 9) on treatment and pre-treatment PTV (wave 9)

short_models <-
  party_codes |>
  lapply(function(party) {
    pre_var <- paste0("ptv_w9_pre_", party)
    post_var <- paste0("ptv_w9_post_", party)

    fml <- paste0(post_var, " ~ workshop * ", pre_var) |>
      as.formula()

    lm_robust(fml, data = df_w9_w10) |>
      tidy()
  }) |>
  bind_rows(.id = "party") |>
  dplyr::filter(term == "workshop")

# Create  plot with confidence intervals
ptv_short <- 
  plot_change(
  results = short_models,
  subtitle = "Effect of treatment on short term support, conditional on initial support")

  
print(ptv_short)

ggsave(
  filename = file.path(fig_dir, "party_support_ptv_shortterm.pdf"),
  plot = ptv_short,
  device = cairo_pdf
)

```

```{r}
#| label: analysis-shortterm-ptv-plot-by-id
#| fig-height: 7
#| fig-width: 7

# Short-term PTV effects by party, split by wave 9 identifiers

ptv_short_by_id_raw <-
  party_codes |>
  lapply(function(party) {
    pre_var <- paste0("ptv_w9_pre_", party)
    post_var <- paste0("ptv_w9_post_", party)
    id_var  <- paste0("party_id_w9_", party)

    fml <- paste0(post_var, " ~ workshop * ", pre_var) |>
      as.formula()

    # All respondents (conditional on continuous baseline PTV)
    m_all <- lm_robust(fml, data = df_w9_w10)

    # Among identifiers (party ID at wave 9 == 1)
    m_id <- lm_robust(
      fml,
      data = df_w9_w10 |> dplyr::filter(!!rlang::sym(id_var) == 1)
    )

    # Among non-identifiers (party ID at wave 9 == 0)
    m_non <- lm_robust(
      fml,
      data = df_w9_w10 |> dplyr::filter(!!rlang::sym(id_var) == 0)
    )

    dplyr::bind_rows(
      tidy(m_all) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "All respondents"),
      tidy(m_id)  |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Identifiers"),
      tidy(m_non) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Non-identifiers")
    ) |>
      dplyr::mutate(party = party_names[[party]])
  }) |>
  dplyr::bind_rows()

party_order_short <-
  ptv_short_by_id_raw |>
  dplyr::filter(group == "All respondents") |>
  dplyr::arrange(estimate) |>
  dplyr::pull(party)

ptv_short_by_id <-
  ptv_short_by_id_raw |>
  dplyr::mutate(
    party = factor(party, levels = party_order_short),
    group = factor(
      group,
      levels = c("All respondents", "Identifiers", "Non-identifiers")
    )
  )

fig_shortterm_ptv_by_id <-
  ptv_short_by_id |>
  ggplot(aes(x = estimate, y = party, color = group)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_point(position = position_dodge(width = 0.6), size = 2.5) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.6),
    height = 0.2
  ) +
  geom_text(
    aes(
      label = sprintf("%.3f (p = %.3f)", estimate, p.value),
      group = group
    ),
    position = position_dodge(width = 0.6),
    hjust = 0.5,
    vjust = -0.7,
    size = 2.5,
    show.legend = FALSE
  ) +
  labs(
    x = "Effect of workshop on short-term PTV (wave 9, 0–1 scale)",
    y = "Party",
    color = NULL,
    title = "Short-term PTV effects of digital literacy workshop",
    subtitle = "Average effect, identifiers, and non-identifiers"
  ) +
  theme_bw()

fig_shortterm_ptv_by_id

ggsave(
  filename = "figs/fig_shortterm_ptv_by_id.pdf",
  plot = fig_shortterm_ptv_by_id,
  width = 7,
  height = 9,
  device = cairo_pdf
)
```



### long term PTV change

```{r}
#| label: analysis-longterm-ptv-plot


long_models <-
  party_codes |>
  lapply(function(party) {
    pre_var <- paste0("ptv_w9_pre_", party)
    post_var <- paste0("ptv_w10_", party)

    fml <- paste0(
      post_var, " ~ workshop * ", pre_var) |>
      as.formula()

    lm_robust(fml, data = df_w9_w10) |>
      tidy()
  }) |>
  bind_rows(.id = "party") |>
  dplyr::filter(term == "workshop")

# Create  plot with confidence intervals
ptv_long <- 
  plot_change(
  results = long_models,
  subtitle = "Effect of treatment on long term PTV, conditional on initial support")

  
print(ptv_long)

ggsave(
  filename = file.path(fig_dir, "party_support_ptv_longterm.pdf"),
  plot = ptv_long,
  device = cairo_pdf
)

```

```{r}
#| label: analysis-longterm-ptv-plot-by-id
#| fig-height: 7
#| fig-width: 7

# Long-term PTV effects by party, split by wave 9 identifiers

ptv_long_by_id_raw <-
  party_codes |>
  lapply(function(party) {
    pre_var <- paste0("ptv_w9_pre_", party)
    post_var <- paste0("ptv_w10_", party)
    id_var  <- paste0("party_id_w9_", party)

    fml <- paste0(post_var, " ~ workshop * ", pre_var) |>
      as.formula()

    # All respondents (conditional on continuous baseline PTV)
    m_all <- lm_robust(fml, data = df_w9_w10)

    # Among identifiers (party ID at wave 9 == 1)
    m_id <- lm_robust(
      fml,
      data = df_w9_w10 |> dplyr::filter(!!rlang::sym(id_var) == 1)
    )

    # Among non-identifiers (party ID at wave 9 == 0)
    m_non <- lm_robust(
      fml,
      data = df_w9_w10 |> dplyr::filter(!!rlang::sym(id_var) == 0)
    )

    dplyr::bind_rows(
      tidy(m_all) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "All respondents"),
      tidy(m_id)  |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Identifiers"),
      tidy(m_non) |> dplyr::filter(term == "workshop") |>
        dplyr::mutate(group = "Non-identifiers")
    ) |>
      dplyr::mutate(party = party_names[[party]])
  }) |>
  dplyr::bind_rows()

party_order_long <-
  ptv_long_by_id_raw |>
  dplyr::filter(group == "All respondents") |>
  dplyr::arrange(estimate) |>
  dplyr::pull(party)

ptv_long_by_id <-
  ptv_long_by_id_raw |>
  dplyr::mutate(
    party = factor(party, levels = party_order_long),
    group = factor(
      group,
      levels = c("All respondents", "Identifiers", "Non-identifiers")
    )
  )

fig_longterm_ptv_by_id <-
  ptv_long_by_id |>
  ggplot(aes(x = estimate, y = party, color = group)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_point(position = position_dodge(width = 0.6), size = 2.5) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.6),
    height = 0.2
  ) +
  geom_text(
    aes(
      label = sprintf("%.3f (p = %.3f)", estimate, p.value),
      group = group
    ),
    position = position_dodge(width = 0.6),
    hjust = 0.5,
    vjust = -0.7,
    size = 2.5,
    show.legend = FALSE
  ) +
  labs(
    x = "Effect of workshop on long-term PTV (wave 10, 0–1 scale)",
    y = "Party",
    color = NULL,
    title = "Long-term PTV effects of digital literacy workshop",
    subtitle = "Average effect, identifiers, and non-identifiers"
  ) +
  theme_bw()

fig_longterm_ptv_by_id

ggsave(
  filename = "figs/fig_longterm_ptv_by_id.pdf",
  plot = fig_longterm_ptv_by_id,
  width = 7,
  height = 9,
  device = cairo_pdf
)
```


## Appendix K: Changes in Party Identification

```{r}
#| label: analysis-pid-change-overall

options(scipen = 999)  # discourage scientific notation

pid_overall <- build_pid_lodes(df_w9_w10)

fig_pid_change <- plot_pid_alluvial(
  lodes = pid_overall$lodes,
  party_cols = pid_overall$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change.pdf"),
  plot = fig_pid_change,
  device = cairo_pdf
)
```


### within treatment

```{r}
#| label: analysis-pid-change-treated

pid_treat <- build_pid_lodes(df_w9_w10 |> filter(workshop == 1))

fig_pid_change_treat <- plot_pid_alluvial(
  lodes = pid_treat$lodes,
  party_cols = pid_treat$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change_treat)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change_treat.pdf"),
  plot = fig_pid_change_treat,
  device = cairo_pdf
)
```

### within control

```{r}
#| label: analysis-pid-change-control

pid_control <- build_pid_lodes(df_w9_w10 |> filter(workshop == 0))

fig_pid_change_control <- plot_pid_alluvial(
  lodes = pid_control$lodes,
  party_cols = pid_control$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change_control)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change_control.pdf"),
  plot = fig_pid_change_control,
  device = cairo_pdf
)

```


## Appendix L: Correlations between short term and long term outcomes

Correlation structure among outcomes by treatment and wave. Ellipses indicate sign and strength; red/blue color encodes sign.

```{r}
#| label: analysis-outcome-correlations

# Compute correlations for both waves (within wave, by treatment)
cor_w9 <- build_cor_df(datasets$wave_9, "Short-term")
cor_w10 <- build_cor_df(datasets$wave_10, "Long-term")

cor_long <- bind_rows(cor_w9, cor_w10) |>
  mutate(sign = ifelse(r >= 0, "positive", "negative"))

# Prepare indices for grid positions
var_levels <- names(v_outcomes)
cor_long <- cor_long |>
  mutate(
    x_idx = match(var2, var_levels),
    y_idx = match(var1, var_levels)
  )

# Upper triangle: filled ellipses inside cells, scaled to avoid overlap
scale_in_cell <- 0.42
ellipse_upper <- cor_long |>
  filter(y_idx < x_idx) |>
  group_by(wave, treat, var1, var2, r, x_idx, y_idx, sign) |>
  do({
    rr <- .$r[1]
    S <- matrix(c(1, rr, rr, 1), nrow = 2)
    e <- as.data.frame(ellipse::ellipse(S, centre = c(0, 0), level = 0.68, npoints = 80))
    # normalize to unit box then scale to cell fraction
    maxabs <- max(max(abs(e$x)), max(abs(e$y)), 1e-9)
    e$x <- (e$x / maxabs) * scale_in_cell + .$x_idx[1]
    e$y <- (e$y / maxabs) * scale_in_cell + .$y_idx[1]
    e$wave <- .$wave[1]
    e$treat <- .$treat[1]
    e$var1 <- .$var1[1]
    e$var2 <- .$var2[1]
    e$sign <- .$sign[1]
    e$r <- rr
    e
  }) |>
  ungroup()

# Lower triangle: numeric labels
label_lower <- cor_long |>
  filter(y_idx > x_idx) |>
  mutate(label = sprintf("%.2f", r))

# Diagonal: blanks (or could set to 1.00 if desired)

p_cor <- ggplot() +
  geom_polygon(
    data = ellipse_upper,
    aes(x = x, y = y, group = interaction(wave, treat, var1, var2), fill = sign),
    color = NA, alpha = 0.75
  ) +
  geom_text(
    data = label_lower,
    aes(x = x_idx, y = y_idx, label = label, color = sign),
    size = 3
  ) +
  scale_fill_manual(values = c(positive = "#d73027", negative = "#4575b4"), name = "Sign") +
  scale_color_manual(values = c(positive = "#d73027", negative = "#4575b4"), guide = "none") +
  scale_x_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  scale_y_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  coord_fixed() +
  labs(x = NULL, y = NULL) +
  theme_tiktok() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  facet_grid(rows = vars(treat), cols = vars(wave))

print(p_cor)
ggsave(
  filename = file.path(
    fig_dir,
    paste0("correlation_ellipses.pdf")
  ),
  plot = p_cor,
  width = 9,
  height = 7,
  device = cairo_pdf
)
```


## Comment classification


```{r ,message=FALSE,warning=FALSE}

# Desired order
levels_vec <- c(
  "0 = setup skepticism",
  "1 = platform-focused",
  "2 = content-focused",
  "3 = other/unclear"
)

comments_plot <- comments_df %>%
  mutate(
    scale_label = fct_explicit_na(scale_label, na_level = "NA"),
    scale_label = fct_relevel(scale_label, levels_vec, after = 0) # keep 0–3 in order; "NA" (if present) goes last
  ) %>%
  count(scale_label, name = "n") %>%
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = scale_label, y = pct)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 0.1)),
            vjust = -0.25, size = 4) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    x = NULL, y = "Share of comments",
    title = "Comment classification (percentage of total)"
  ) +
  theme_bw(base_size = 13) +
  theme(panel.grid.major.x = element_blank())

comments_plot
ggsave('figs/fig_classification_comments.pdf', width = 8, height = 4)


```

