---
title: "Digital literacy reduces susceptibility to populist content on social media"
subtitle: Replication data and code
author: Kristina Aleksandrovna Pedersen, Ferdinand Geissler, Felix Hartmann, Johannes Giesecke, Macartan Humphreys, Heike Klüver
format:
  html:
    number-sections: true
    embed-resources: true
    code-fold: true
    toc: true
execute:
  echo: true
  warning: true
  message: false
---


# Setup

```{r}
#| label: analysis-setup-packages

# Load packages
pacman::p_load(fixest, tidyverse, DeclareDesign, haven, knitr, broom, ggh4x, ellipse, ggrepel)

```


## Configuration

```{r}
#| label: analysis-configuration

setFixest_notes(FALSE)  # Suppress fixest NOTE messages
filter_10 <- TRUE
pref_var <- "party_preference_"

# Edit figure labels here
strategies <- 
  c("political\n(emotional)", "political\n(neutral)")

# Unified output directories
fig_dir <- "figs"

# Filename suffix by wave
wave_suffix <- c(
  wave_9 = "_shortterm",
  wave_10 = "_longterm"
)

# Outcomes and groups
v_outcomes <- c(
  "Like" = "videoLikep1r",
  "Share" = "videoSharep1r",
  "Bookmark" = "videoBookmarkp1r",
  "Report" = "videoCommentTickedp1r",
  "Watch Time" = "watch_percentage_",
  "Skip" = "skipped_video_"
)

l_outcomegroups <- list(
  main = c("Like", "Report", "Share", "Bookmark"),
  "_other" = c("Skip", "Watch Time")
)

l_partisanship <- list(
  "Supporter: Yes" = 1,
  "Supporter: No" = 0,
  "All" = c(0, 1)
)

ps <- tibble(
  parties = c("AfD", "BSW", "CDU/CSU", "FDP", "Grüne", "Linke", "SPD"),
  party_stub = c("afd", "bsw", "cdu", "fdp", "gruene", "linke", "spd")
)
```


## Helper functions

```{r}
#| label: analysis-helper-functions
# Plot helpers

gg_coefplot <- function(data, aes) {
  ggplot(data, aes) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_point() +
    geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
    theme_tiktok() +
    scale_color_tiktok()
}

# Theme and palette

theme_tiktok <- function() {
  theme_bw() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
    )
}

scale_color_tiktok <- function() {
  scale_color_discrete()
}
```


# Data 

```{r}
#| label: integrity

datasets <- list(
  wave_9  = read_rds("data/wave_9.rds"),
  wave_10 = read_rds("data/wave_10.rds")
)

individual_df <- 
  left_join(
  datasets$wave_9 |> group_by(ID) |> 
  summarize(Z9 = mean(workshop_Treatment, na.rm = TRUE),
            afd9 = mean(party_preference_afd, na.rm = TRUE),
            cdu9 = mean(party_preference_cdu, na.rm = TRUE),
            linke9 = mean(party_preference_linke, na.rm = TRUE),
            spd9 = mean(party_preference_spd, na.rm = TRUE),
            gruene9 = mean(party_preference_gruene, na.rm = TRUE),
            fdp9 = mean(party_preference_fdp, na.rm = TRUE),
            bsw9 = mean(party_preference_bsw, na.rm = TRUE),
            liker9 = mean(videoLikep1r, na.rm = TRUE),
            n9 = n(),
            tiktok_user = mean(TikTok_User)),
  
  datasets$wave_10 |> group_by(ID) |> 
  summarize(Z10 = mean(workshop_Treatment, na.rm = TRUE),
            afd10 = mean(party_preference_afd, na.rm = TRUE),
            linke10 = mean(party_preference_linke, na.rm = TRUE),
            cdu10 = mean(party_preference_cdu, na.rm = TRUE),
            spd10 = mean(party_preference_spd, na.rm = TRUE),
            gruene10 = mean(party_preference_gruene, na.rm = TRUE),
            fdp10 = mean(party_preference_fdp, na.rm = TRUE),
            bsw10 = mean(party_preference_bsw, na.rm = TRUE),
            liker10 = mean(videoLikep1r, na.rm = TRUE),
            n10 = n())
  ) |> 
  mutate(missing = is.na(Z10))  
```



# Main Results (Figure 1, 4, 5, and associated appendix figures)

Treatment effects by high-level video content types and displays/saves coefficient plots per outcome.

```{r}
#| label: analysis-main-results
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_I <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(unique(df$strategy_2), function(S)
        feols(
          as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
          data = df |> filter(strategy_2 == S),
          cluster = ~ID
        ) |>
          tidy(conf.int = TRUE) |>
          mutate(outcome = Y, strategy = S)
      ) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_I <- df_f_I |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_I)
    ggsave(
      filename = paste0(
        fig_dir, "/f_I", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_I,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}

```


# Conditional on sender (Figure 2 and related appendix figure)

Treatment effects within each party for political content types, per outcome.

```{r}
#| label: analysis-conditional-on-sender
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIa <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(ps$parties, function(P)
          feols(
            as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
            data = df |> filter(strategy_2 == S, party == P),
            cluster = ~ID
          ) |>
            tidy(conf.int = TRUE) |>
            mutate(outcome = Y, strategy = S, party = P)
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIa <- df_f_IIa |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(party)) +
      labs(title = wave_label)

    print(gg_f_IIa)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIa", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIa,
      width = 7,
      height = 6,
      device = cairo_pdf
    )
  }
}
```


# By partisanship (Figure 3 and related appendix figures)

This section estimates treatment effects by partisanship grouping (supporter yes/no/all) within political content types, per outcome.

```{r}
#| label: analysis-by-partisanship
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS)
          lapply(ps$parties, function(P)
            feols(
              as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
              data = df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]]),
              cluster = ~ID
            ) |>
              tidy(conf.int = TRUE) |>
              mutate(outcome = Y, strategy = S, partisan = PS)
          ) |> bind_rows()) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc <- df_f_IIc |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(partisan)) +
      labs(title = wave_label)

    print(gg_f_IIc)
    ggsave(filename = paste0(fig_dir, "/f_IIc", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"), 
           plot = gg_f_IIc, width = 7, height = 6, 
           device = cairo_pdf)
  }
}
```




# Other appendix items

## A Descriptives

## C Coding of TikTok videos

## G Engagement with platform

## H Further analysis

### By strategy

This section estimates treatment effects by specific emotional strategies (anger, fear, superiority), per outcome.

* saved as f_IIb files 

```{r}
#| label: analysis-by-strategy
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIb <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(c("anger", "fear", "superiority"), function(S)
        feols(
          as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
          data = df |> filter(strategy == S),
          cluster = ~ID
        ) |>
          tidy(conf.int = TRUE) |>
          mutate(outcome = Y, strategy = S)
      ) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIb <- df_f_IIb |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_IIb)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIb", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIb,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}
```


### f_IIc3: by partisanship and party

This section estimates treatment effects by party and partisanship, with nested facet labels.

```{r}
#| label: analysis-f_IIc3-partisanship-party
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3 <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS)
          lapply(ps$parties, function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " 
                          (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            feols(
              as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
              data = df_temp,
              cluster = ~ID
            ) |>
              tidy(conf.int = TRUE) |>
              mutate(outcome = Y, strategy = S, partisan = as.character(PS), party = P)
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3 <- df_f_IIc3 |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none",
        axis.text = element_text(size = 6.5)
      )

    print(gg_f_IIc3)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3,
      width = 7,
      height = 11,
      device = cairo_pdf
    )
  }
}
```


### f_IIc3b: by partisanship and party (alternate)

This alternate visualization repeats f_IIc3 but shows only supporter yes/no levels.

```{r}
#| label: analysis-f_IIc3b-partisanship-party-alt
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3b <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship[1:2]), function(PS)
          lapply(ps$parties, function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            feols(
              as.formula(paste(v_outcomes[Y], "~ workshop_Treatment | video")),
              data = df_temp,
              cluster = ~ID
            ) |>
              tidy(conf.int = TRUE) |>
              mutate(outcome = Y, strategy = S, partisan = as.character(PS), party = P)
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3b <- df_f_IIc3b |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none"
      )

    print(gg_f_IIc3b)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3b", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3b,
      width = 7,
      height = 8,
      device = cairo_pdf
    )
  }
}
```



## Attrition analysis

## Downstream effects on AfD support 

## Maintained support?

```{r}
#| label: analysis-maintained-support
#| results: asis
#| include: false
party_support <- list(
  lm_robust(afd10 ~ afd9 * Z9, data = individual_df),
  lm_robust(cdu10 ~ cdu9 * Z9, data = individual_df),
  lm_robust(linke10 ~ linke9 * Z9, data = individual_df)
  )

party_support |> texreg::htmlreg()

```

```{r}
#| label: analysis-party-support-arrows
# Calculate mean party support by treatment group for arrow plot
arrow_data <- individual_df |> 
  group_by(Z9) |> 
  summarize(
    afd_w9 = mean(afd9, na.rm = TRUE),
    afd_w10 = mean(afd10, na.rm = TRUE),
    cdu_w9 = mean(cdu9, na.rm = TRUE), 
    cdu_w10 = mean(cdu10, na.rm = TRUE),
    linke_w9 = mean(linke9, na.rm = TRUE),
    linke_w10 = mean(linke10, na.rm = TRUE),
    spd_w9 = mean(spd9, na.rm = TRUE),
    spd_w10 = mean(spd10, na.rm = TRUE),
    gruene_w9 = mean(gruene9, na.rm = TRUE),
    gruene_w10 = mean(gruene10, na.rm = TRUE),
    fdp_w9 = mean(fdp9, na.rm = TRUE),
    fdp_w10 = mean(fdp10, na.rm = TRUE),
    bsw_w9 = mean(bsw9, na.rm = TRUE),
    bsw_w10 = mean(bsw10, na.rm = TRUE)
  ) |> 
  mutate(treatment = ifelse(Z9 == 1, "Treatment", "Control"))

# Reshape to long format for plotting
arrow_long <- arrow_data |> 
  select(treatment, afd_w9, afd_w10, cdu_w9, cdu_w10, linke_w9, linke_w10, 
         spd_w9, spd_w10, gruene_w9, gruene_w10, fdp_w9, fdp_w10, bsw_w9, bsw_w10) |> 
  pivot_longer(cols = -treatment, names_to = "party_wave", values_to = "support") |> 
  separate(party_wave, into = c("party", "wave"), sep = "_w") |> 
  pivot_wider(names_from = wave, values_from = support, names_prefix = "w") |> 
  mutate(party = case_when(
    party == "afd" ~ "AfD",
    party == "cdu" ~ "CDU/CSU", 
    party == "linke" ~ "Linke",
    party == "spd" ~ "SPD",
    party == "gruene" ~ "Grüne",
    party == "fdp" ~ "FDP",
    party == "bsw" ~ "BSW"
  ))

# Create arrow plot
p_arrows <- ggplot(arrow_long, aes(x = w9, y = w10)) +
  geom_point(aes(color = treatment), size = 3, alpha = 0.7) +
  geom_segment(
    data = arrow_long |> 
      pivot_wider(names_from = treatment, values_from = c(w9, w10)) |> 
      filter(!is.na(w9_Control) & !is.na(w9_Treatment)),
    aes(x = w9_Control, y = w10_Control, 
        xend = w9_Treatment, yend = w10_Treatment),
    arrow = arrow(length = unit(0.2, "cm")), 
    color = "black", size = 1
  ) +
  geom_text_repel(
    aes(label = ifelse(treatment == "Control", party, "")),
    size = 3, force = 2, color = "black"
  ) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    x = "Party Support in Wave 9", 
    y = "Party Support in Wave 10",
    title = "Changes in Party Support: Control vs Treatment",
    subtitle = "Arrows show movement from Control to Treatment group means"
  ) +
  scale_color_manual(values = c("Control" = "#F8766D", "Treatment" = "#00BFC4")) +
  theme_bw() +
  theme(legend.title = element_blank())

print(p_arrows)
```

```{r}
#| label: analysis-did-plot-example
#| eval: false
# Create difference-in-differences plot
# Calculate change from W9 to W10 for each party and treatment group
did_data <- arrow_long |> 
  mutate(change = w10 - w9) |> 
  select(party, treatment, change) |> 
  pivot_wider(names_from = treatment, values_from = change) |> 
  mutate(
    did_effect = Treatment - Control,  # Difference-in-difference
    party_label = party
  )

# Create the DiD plot
p_did <- ggplot(did_data, aes(x = reorder(party, did_effect), y = did_effect)) +
  geom_col(aes(fill = ifelse(did_effect > 0, "Positive", "Negative")), 
           alpha = 0.7, width = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_text(aes(label = sprintf("%.3f", did_effect)), 
            hjust = ifelse(did_data$did_effect > 0, -0.1, 1.1), 
            size = 3.5) +
  scale_fill_manual(values = c("Positive" = "#2E8B57", "Negative" = "#DC143C")) +
  labs(
    x = "Party",
    y = "Difference-in-Difference Effect",
    title = "Treatment Effects on Party Support Changes",
    subtitle = "DiD = (Treatment W9→W10 change) - (Control W9→W10 change)",
    caption = "Positive values indicate treatment increased support change relative to control"
  ) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.subtitle = element_text(size = 9)
  ) +
  coord_flip()

print(p_did)
```

```{r}
#| label: analysis-did-ci-plot
# Create DiD plot with confidence intervals using simple regressions
# Fit simple DiD regressions for each party (change in support)
did_models <- map_dfr(c("afd", "cdu", "linke", "spd", "gruene", "fdp", "bsw"), function(party) {
  
  # Create party-specific data with change in support
  party_data <- individual_df |> 
    select(ID, Z9, 
           w9 = paste0(party, "9"), 
           w10 = paste0(party, "10")) |> 
    filter(!is.na(w9) & !is.na(w10)) |> 
    mutate(w9_demean = w9 - mean(w9))  # Change in support from W9 to W10
  
  # Fit simple DiD model: change ~ treatment
  model <- lm(w10 ~ Z9*w9_demean, data = party_data)
  
  # Extract treatment coefficient (DiD effect)
  coef_summary <- summary(model)$coefficients
  
  tibble(
    party = case_when(
      party == "afd" ~ "AfD",
      party == "cdu" ~ "CDU/CSU",
      party == "linke" ~ "Linke", 
      party == "spd" ~ "SPD",
      party == "gruene" ~ "Grüne",
      party == "fdp" ~ "FDP",
      party == "bsw" ~ "BSW"
    ),
    did_effect = coef_summary["Z9", "Estimate"],
    se = coef_summary["Z9", "Std. Error"],
    conf_low = did_effect - 1.96 * se,
    conf_high = did_effect + 1.96 * se,
    p_value = coef_summary["Z9", "Pr(>|t|)"]
  )
})

# Create  plot with confidence intervals
p_ci <- ggplot(did_models |> filter(!is.na(did_effect)), 
                   aes(x = reorder(party, did_effect), y = did_effect)) +
  geom_col(aes(fill = ifelse(did_effect > 0, "Positive", "Negative")), 
           alpha = 0.7, width = 0.6) +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high), 
                width = 0.2, color = "black", size = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_text(aes(label = sprintf("%.3f\n(p=%.3f)", did_effect, p_value)), 
            hjust = ifelse(did_models$did_effect > 0, -0.1, 1.1), 
            size = 2.8) +
  scale_fill_manual(values = c("Positive" = "#2E8B57", "Negative" = "#DC143C")) +
  labs(
    x = "Party",
    y = "Change in support",
    title = "Treatment Effects (with 95% CI)",
    subtitle = "Effect of treatment on long term support, conditional on initial support",
    caption = "Error bars show 95% confidence intervals."
  ) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.subtitle = element_text(size = 9),
    plot.caption = element_text(size = 8)
  ) +
  coord_flip()

print(p_ci)

```

## Changes in Party Identification

## Correlations between short term and long term outcomes

Correlation structure among outcomes by treatment and wave. Ellipses indicate sign and strength; red/blue color encodes sign.

```{r}
#| label: analysis-outcome-correlations
# Build a long data frame of correlations by wave and treatment
build_cor_df <- function(df, wave_label) {
  groups <- list(
    list(treat = "Treated", data = df |> filter(workshop_Treatment == 1)),
    list(treat = "Control", data = df |> filter(workshop_Treatment == 0))
  )
  purrr::map_df(groups, function(x) {
    df_sel <- x$data |> select(all_of(v_outcomes))
    colnames(df_sel) <- names(v_outcomes)
    cmat <- cor(df_sel, use = "pairwise.complete.obs")
    as.data.frame(as.table(cmat)) |>
      rename(var1 = Var1, var2 = Var2, r = Freq) |>
      mutate(treat = x$treat, wave = wave_label)
  })
}

# Compute correlations for both waves
cor_w9 <- build_cor_df(datasets$wave_9, "Short-term")
cor_w10 <- build_cor_df(datasets$wave_10, "Long-term")

cor_long <- bind_rows(cor_w9, cor_w10) |>
  mutate(sign = ifelse(r >= 0, "positive", "negative"))

# Prepare indices for grid positions
var_levels <- names(v_outcomes)
cor_long <- cor_long |>
  mutate(
    x_idx = match(var2, var_levels),
    y_idx = match(var1, var_levels)
  )

# Upper triangle: filled ellipses inside cells, scaled to avoid overlap
scale_in_cell <- 0.42
ellipse_upper <- cor_long |>
  filter(y_idx < x_idx) |>
  group_by(wave, treat, var1, var2, r, x_idx, y_idx, sign) |>
  do({
    rr <- .$r[1]
    S <- matrix(c(1, rr, rr, 1), nrow = 2)
    e <- as.data.frame(ellipse::ellipse(S, centre = c(0, 0), level = 0.68, npoints = 80))
    # normalize to unit box then scale to cell fraction
    maxabs <- max(max(abs(e$x)), max(abs(e$y)), 1e-9)
    e$x <- (e$x / maxabs) * scale_in_cell + .$x_idx[1]
    e$y <- (e$y / maxabs) * scale_in_cell + .$y_idx[1]
    e$wave <- .$wave[1]
    e$treat <- .$treat[1]
    e$var1 <- .$var1[1]
    e$var2 <- .$var2[1]
    e$sign <- .$sign[1]
    e$r <- rr
    e
  }) |>
  ungroup()

# Lower triangle: numeric labels
label_lower <- cor_long |>
  filter(y_idx > x_idx) |>
  mutate(label = sprintf("%.2f", r))

# Diagonal: blanks (or could set to 1.00 if desired)

p_cor <- ggplot() +
  geom_polygon(
    data = ellipse_upper,
    aes(x = x, y = y, group = interaction(wave, treat, var1, var2), fill = sign),
    color = NA, alpha = 0.75
  ) +
  geom_text(
    data = label_lower,
    aes(x = x_idx, y = y_idx, label = label, color = sign),
    size = 3
  ) +
  scale_fill_manual(values = c(positive = "#d73027", negative = "#4575b4"), name = "Sign") +
  scale_color_manual(values = c(positive = "#d73027", negative = "#4575b4"), guide = "none") +
  scale_x_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  scale_y_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  coord_fixed() +
  labs(x = NULL, y = NULL) +
  theme_tiktok() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  facet_grid(rows = vars(treat), cols = vars(wave))

print(p_cor)
ggsave(
  filename = file.path(
    fig_dir,
    paste0("correlation_ellipses.pdf")
  ),
  plot = p_cor,
  width = 9,
  height = 7,
  device = cairo_pdf
)
```
