---
title: "Digital literacy reduces susceptibility to populist content on social media"
subtitle: Replication data and code
author: Kristina Aleksandrovna Pedersen, Ferdinand Geissler, Felix Hartmann, Johannes Giesecke, Macartan Humphreys, Heike Klüver
format:
  html:
    number-sections: true
    embed-resources: true
    code-fold: true
    toc: true
execute:
  echo: true
  warning: true
  message: false
---


# Setup

```{r}
#| label: analysis-setup-packages

# Load packages
pacman::p_load(
  forcats,
  scales,
  fixest,
  tidyverse,
  DeclareDesign,
  haven,
  knitr,
  broom,
  ggh4x,
  ellipse,
  ggrepel,
  texreg,
  ggalluvial,
  scales
)

```


## Configuration

```{r}
#| label: analysis-configuration

setFixest_notes(FALSE)  # Suppress fixest NOTE messages
filter_10 <- TRUE
pref_var <- "party_preference_"

# Edit figure labels here
strategies <- 
  c("political\n(emotional)", "political\n(neutral)")

# Unified output directories
fig_dir <- "figs"

# Filename suffix by wave
wave_suffix <- c(
  wave_9 = "_shortterm",
  wave_10 = "_longterm"
)

# Outcomes and groups
v_outcomes <- c(
  "Like" = "videoLikep1r",
  "Share" = "videoSharep1r",
  "Bookmark" = "videoBookmarkp1r",
  "Report" = "videoCommentTickedp1r",
  "Watch Time" = "watch_percentage_",
  "Skip" = "skipped_video_"
)

l_outcomegroups <- list(
  main = c("Like", "Report", "Share", "Bookmark"),
  "_other" = c("Skip", "Watch Time")
)

l_partisanship <- list(
  "Supporter: Yes" = 1,
  "Supporter: No" = 0,
  "All" = c(0, 1)
)

ps <- tibble(
  parties = c("AfD", "BSW", "CDU/CSU", "FDP", "Grüne", "Linke", "SPD"),
  party_stub = c("afd", "bsw", "cdu", "fdp", "gruene", "linke", "spd")
)
```


## Helper functions

```{r}
#| label: analysis-helper-functions
# Plot helpers

gg_coefplot <- function(data, aes) {
  ggplot(data, aes) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_point() +
    geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
    theme_tiktok() +
    scale_color_tiktok()
}

# Theme and palette

theme_tiktok <- function() {
  theme_bw() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
    )
}

scale_color_tiktok <- function() {
  scale_color_discrete()
}

party_label <- function(code) {
  dplyr::case_when(
    code == "afd" ~ "AfD",
    code == "cdu" ~ "CDU/CSU",
    code == "linke" ~ "Linke",
    code == "spd" ~ "SPD",
    code == "gruene" ~ "Grüne",
    code == "fdp" ~ "FDP",
    code == "bsw" ~ "BSW",
    TRUE ~ code
  )
}

# Party identification transition helpers
build_pid_lodes <- function(df_input) {
  labs <- c(
    cdu = "CDU/CSU",
    spd = "SPD",
    gruene = "Grüne",
    fdp = "FDP",
    linke = "Linke",
    afd = "AfD",
    bsw = "BSW",
    none = "Non-Voters",
    other = "Other"
  )

  from <- df_input |>
    select(id_w9, starts_with("party_id_") & ends_with("_w9")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      from_party = recode(
        sub("^party_id_(.*)_w9$", "\\1", var),
        !!!labs
      )
    )

  to <- df_input |>
    select(id_w9, starts_with("party_id_") & ends_with("_w10")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      to_party = recode(
        sub("^party_id_(.*)_w10$", "\\1", var),
        !!!labs
      )
    )

  transitions_indiv <- inner_join(from, to, by = "id_w9")

  transitions <- transitions_indiv |>
    count(`Wave 9` = from_party, `Wave 10` = to_party, name = "Freq")

  totN <- sum(transitions$Freq)

  share_w9 <- transitions |>
    group_by(`Wave 9`) |>
    summarise(s9 = sum(Freq) / totN, .groups = "drop")

  share_w10 <- transitions |>
    group_by(`Wave 10`) |>
    summarise(s10 = sum(Freq) / totN, .groups = "drop")

  net_pp <- share_w10 |>
    left_join(share_w9, by = c("Wave 10" = "Wave 9")) |>
    mutate(
      delta_pp = (s10 - s9) * 100,
      label_right = sprintf("%s\n(%+0.2f pp)", `Wave 10`, delta_pp)
    ) |>
    select(`Wave 10`, label_right)

  lodes <- transitions |>
    mutate(Share = Freq / totN) |>
    to_lodes_form(axes = 1:2, id = "alluvium") |>
    mutate(
      x = factor(x, levels = c("Wave 9", "Wave 10")),
      stratum_lab = ifelse(
        x == "Wave 10",
        net_pp$label_right[match(stratum, net_pp$`Wave 10`)],
        as.character(stratum)
      )
    )

  party_cols <- c(
    "CDU/CSU" = "#000000",
    "SPD" = "#E3000F",
    "Grüne" = "#0DB02B",
    "FDP" = "#FFED00",
    "Linke" = "#E2382A",
    "AfD" = "#009EE0",
    "BSW" = "#18A19A"
  )

  list(lodes = lodes, party_cols = party_cols)
}

plot_pid_alluvial <- function(lodes, party_cols, title_text) {
  ggplot(
    lodes,
    aes(
      x = x,
      stratum = stratum,
      alluvium = alluvium,
      y = Share,
      fill = stratum,
      label = stratum_lab
    )
  ) +
    geom_alluvium(alpha = 0.7, color = NA, knot.pos = 0.4) +
    geom_stratum(fill = "white", color = "black", size = 0.3) +
    geom_text(stat = "stratum", size = 4) +
    scale_fill_manual(values = party_cols, guide = "none") +
    scale_x_discrete(
      labels = c("Wave 9", "Wave 10"),
      expand = c(0.05, 0.05)
    ) +
    labs(
      x = NULL,
      y = NULL,
      title = title_text
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      panel.grid = element_blank(),
      axis.text.y = element_blank()
    )
}

# Build correlation data for a single wave and treatment status
build_cor_df <- function(df, wave_label) {
  groups <- list(
    list(treat = "Treated", data = df |> filter(workshop_Treatment == 1)),
    list(treat = "Control", data = df |> filter(workshop_Treatment == 0))
  )
  purrr::map_df(groups, function(x) {
    df_sel <- x$data |> select(all_of(v_outcomes))
    colnames(df_sel) <- names(v_outcomes)
    cmat <- cor(df_sel, use = "pairwise.complete.obs")
    as.data.frame(as.table(cmat)) |>
      rename(var1 = Var1, var2 = Var2, r = Freq) |>
      mutate(treat = x$treat, wave = wave_label)
  })
}

# Attrition helpers
get_interaction <- function(data, v, treat_col = "treated_w9", outcome = "attrit") {
  f <- as.formula(paste0(outcome, " ~ ", treat_col, " * ", v))
  fit <- lm(f, data = data)
  coefs <- summary(fit)$coef
  rname <- intersect(
    rownames(coefs),
    c(
      paste0(treat_col, ":", v),
      paste0(v, ":", treat_col)
    )
  )
  if (!length(rname)) {
    return(NULL)
  }
  est <- coefs[rname, "Estimate"]
  se <- coefs[rname, "Std. Error"]
  p <- coefs[rname, "Pr(>|t|)"]
  data.frame(
    variable = v,
    estimate = est,
    std.error = se,
    p.value = p,
    conf.low = est - 1.96 * se,
    conf.high = est + 1.96 * se,
    n = stats::nobs(fit)
  )
}

compute_attrition_results <- function(data, covariates, treat_col = "treated_w9", outcome = "attrit") {
  do.call(
    rbind,
    lapply(
      covariates,
      function(v) {
        tryCatch(
          get_interaction(
            data = data,
            v = v,
            treat_col = treat_col,
            outcome = outcome
          ),
          error = function(e) NULL
        )
      }
    )
  )
}

# English labels for covariates (matches df after tolower)
labels_en <- c(
  # basics
  alter = "Age",
  geschlecht = "Gender",
  citysize = "City size",

  # region binaries & state dummies
  east = "East (vs West)",
  saxony = "Saxony (state dummy)",
  state_baden_wuerttemberg = "State: Baden-Württemberg",
  state_bayern = "State: Bavaria",
  state_berlin = "State: Berlin",
  state_brandenburg = "State: Brandenburg",
  state_bremen = "State: Bremen",
  state_hamburg = "State: Hamburg",
  state_hessen = "State: Hesse",
  state_mecklenburg_vorpommern = "State: Mecklenburg–Western Pomerania",
  state_niedersachsen = "State: Lower Saxony",
  state_nordrhein_westfalen = "State: North Rhine–Westphalia",
  state_rheinland_pfalz = "State: Rhineland–Palatinate",
  state_saarland = "State: Saarland",
  state_sachsen = "State: Saxony",
  state_sachsen_anhalt = "State: Saxony-Anhalt",
  state_schleswig_holstein = "State: Schleswig-Holstein",
  state_thueringen = "State: Thuringia",

  # urbanization binaries
  urban_ballungsraum = "Urban: Ballungsraum",
  urban_stadtregion = "Urban: Stadtregion",
  urban_mittelzentrum = "Urban: Mittelzentrengebiet",
  urban_high = "Urban (1\u20132) vs Mittelzentrum (3)",

  # social media (post-lowercase names)
  video_userfacebook = "Uses Facebook (video)",
  video_usertiktok = "Uses TikTok (video)",
  video_usersnapchat = "Uses Snapchat (video)",
  video_userpinterest = "Uses Pinterest (video)",
  video_userx_ehem_twitter = "Uses X/Twitter (video)",
  video_usertwitch = "Uses Twitch (video)",

  # attitudes
  politikinteresse = "Political interest",
  competence = "Perceived competence",
  lr = "Left\u2013Right ideology",

  # party ID (w9)
  party_id_cdu_w9 = "Party ID: CDU/CSU",
  party_id_spd_w9 = "Party ID: SPD",
  party_id_afd_w9 = "Party ID: AfD",
  party_id_gruene_w9 = "Party ID: Greens",
  party_id_fdp_w9 = "Party ID: FDP",
  party_id_linke_w9 = "Party ID: The Left",
  party_id_bsw_w9 = "Party ID: BSW",

  # PTV pre (w9)
  ptv_cdu_w9_pre = "PTV CDU/CSU (pre)",
  ptv_spd_w9_pre = "PTV SPD (pre)",
  ptv_linke_w9_pre = "PTV The Left (pre)",
  ptv_gruene_w9_pre = "PTV Greens (pre)",
  ptv_fdp_w9_pre = "PTV FDP (pre)",
  ptv_afd_w9_pre = "PTV AfD (pre)",
  ptv_bsw_w9_pre = "PTV BSW (pre)",

  # other covariates
  prior_performance_general_2 = "Perceived gov't performance (prior)",
  solidaritat = "Solidarity",
  sozialer_zusammenhalt = "Social cohesion",
  migration = "Immigration attitudes",

  # TikTok splits
  tiktok_user_yes = "Current TikTok user",
  tiktok_user_no = "Not a TikTok user",
  tiktok_potential_yes = "Open to get a TikTok account",
  tiktok_potential_no = "Not open to get a TikTok account",

  # sociodemographics
  beruflicher_status = "Employment status",
  berufliche_stellung = "Occupational position",
  bildung_schulisch = "School education",
  bildung_beruflich = "Vocational education",
  eigene_kinder = "Has children",
  haushaltsgrobe = "Household size",
  migrationshintergrund_eltern = "Parental migration background",
  haushaltseinkommen = "Household income"
)

# Run feols by group and return tidied coefficients with metadata
run_feols_tidy <- function(df, outcome_var, extra_cols = list()) {
  feols(
    as.formula(paste(outcome_var, "~ workshop_Treatment | video")),
    data = df,
    cluster = ~ID
  ) |>
    tidy(conf.int = TRUE) |>
    mutate(!!!extra_cols)
}
```


# Data 

```{r}
#| label: integrity

datasets <- list(
  wave_9  = read_rds("data/wave_9.rds"),
  wave_10 = read_rds("data/wave_10.rds")
)

# Defined at individual level
individual_df <- 
  left_join(
  datasets$wave_9 |> group_by(ID) |> 
  summarize(Z9 = mean(workshop_Treatment, na.rm = TRUE),
            afd9 = mean(party_preference_afd, na.rm = TRUE),
            cdu9 = mean(party_preference_cdu, na.rm = TRUE),
            linke9 = mean(party_preference_linke, na.rm = TRUE),
            spd9 = mean(party_preference_spd, na.rm = TRUE),
            gruene9 = mean(party_preference_gruene, na.rm = TRUE),
            fdp9 = mean(party_preference_fdp, na.rm = TRUE),
            bsw9 = mean(party_preference_bsw, na.rm = TRUE),
            liker9 = mean(videoLikep1r, na.rm = TRUE),
            n9 = n(),
            tiktok_user = mean(TikTok_User)),
  
  datasets$wave_10 |> group_by(ID) |> 
  summarize(Z10 = mean(workshop_Treatment, na.rm = TRUE),
            afd10 = mean(party_preference_afd, na.rm = TRUE),
            linke10 = mean(party_preference_linke, na.rm = TRUE),
            cdu10 = mean(party_preference_cdu, na.rm = TRUE),
            spd10 = mean(party_preference_spd, na.rm = TRUE),
            gruene10 = mean(party_preference_gruene, na.rm = TRUE),
            fdp10 = mean(party_preference_fdp, na.rm = TRUE),
            bsw10 = mean(party_preference_bsw, na.rm = TRUE),
            liker10 = mean(videoLikep1r, na.rm = TRUE),
            n10 = n())
  ) |> 
  ungroup() |> 
  mutate(missing = is.na(Z10))  |>
  mutate(
    afd9_demean = afd9 - mean(afd9, na.rm = TRUE),
    cdu9_demean = cdu9 - mean(cdu9, na.rm = TRUE),
    linke9_demean = linke9 - mean(linke9, na.rm = TRUE),
    spd9_demean = spd9 - mean(spd9, na.rm = TRUE),
    gruene9_demean = gruene9 - mean(gruene9, na.rm = TRUE),
    fdp9_demean = fdp9 - mean(fdp9, na.rm = TRUE),
    bsw9_demean = bsw9 - mean(bsw9, na.rm = TRUE))
    

```



# Main Results (Figure 1, 4, 5, and associated appendix figures)

Treatment effects by high-level video content types and displays/saves coefficient plots per outcome.

```{r}
#| label: analysis-main-results
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_I <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(unique(df$strategy_2), function(S) {
        df_sub <- df |> filter(strategy_2 == S)
        run_feols_tidy(
          df = df_sub,
          outcome_var = v_outcomes[Y],
          extra_cols = list(outcome = Y, strategy = S)
        )
      }) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_I <- df_f_I |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_I)
    ggsave(
      filename = paste0(
        fig_dir, "/f_I", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_I,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}

```


# Conditional on sender (Figure 2 and related appendix figure)

Treatment effects within each party for political content types, per outcome.

```{r}
#| label: analysis-conditional-on-sender
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIa <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(ps$parties, function(P) {
          df_sub <- df |> filter(strategy_2 == S, party == P)
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S, party = P)
          )
        }) |>
          bind_rows()
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIa <- df_f_IIa |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(party)) +
      labs(title = wave_label)

    print(gg_f_IIa)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIa", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIa,
      width = 7,
      height = 6,
      device = cairo_pdf
    )
  }
}
```


# By partisanship (Figure 3 and related appendix figures)

This section estimates treatment effects by partisanship grouping (supporter yes/no/all) within political content types, per outcome.

```{r}
#| label: analysis-by-partisanship
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS) {
          df_sub <- df |>
            filter(strategy_2 == S, partisan %in% l_partisanship[[PS]])
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S, partisan = PS)
          )
        }) |>
          bind_rows()
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc <- df_f_IIc |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome), rows = vars(partisan)) +
      labs(title = wave_label)

    print(gg_f_IIc)
    ggsave(filename = paste0(fig_dir, "/f_IIc", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"), 
           plot = gg_f_IIc, width = 7, height = 6, 
           device = cairo_pdf)
  }
}
```




# Other appendix items

## A Descriptives

## C Coding of TikTok videos

## G Engagement with platform

## H Further analysis

### By strategy

This section estimates treatment effects by specific emotional strategies (anger, fear, superiority), per outcome.

* saved as f_IIb files 

```{r}
#| label: analysis-by-strategy
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIb <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(c("anger", "fear", "superiority"), function(S)
        {
          df_sub <- df |> filter(strategy == S)
          run_feols_tidy(
            df = df_sub,
            outcome_var = v_outcomes[Y],
            extra_cols = list(outcome = Y, strategy = S)
          )
        }
      ) |>
        bind_rows()
    ) |>
      bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIb <- df_f_IIb |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_grid(cols = vars(outcome)) +
      labs(title = wave_label)

    print(gg_f_IIb)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIb", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIb,
      width = 7,
      height = 3,
      device = cairo_pdf
    )
  }
}
```


### f_IIc3: by partisanship and party

This section estimates treatment effects by party and partisanship, with nested facet labels.

```{r}
#| label: analysis-f_IIc3-partisanship-party
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3 <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship), function(PS)
          lapply(ps$parties, function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " 
                          (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            run_feols_tidy(
              df = df_temp,
              outcome_var = v_outcomes[Y],
              extra_cols = list(
                outcome = Y,
                strategy = S,
                partisan = as.character(PS),
                party = P
              )
            )
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3 <- df_f_IIc3 |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none",
        axis.text = element_text(size = 6.5)
      )

    print(gg_f_IIc3)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3,
      width = 7,
      height = 11,
      device = cairo_pdf
    )
  }
}
```


###  by partisanship and party (alternate)

suffix: `f_IIc3b`

This alternate visualization repeats f_IIc3 but shows only supporter yes/no levels.

```{r}
#| label: analysis-f_IIc3b-partisanship-party-alt
for (D in c("wave_9", "wave_10")) {
  df <- datasets[[D]]

  for (OG in names(l_outcomegroups)) {
    df_f_IIc3b <- lapply(l_outcomegroups[[OG]], function(Y)
      lapply(strategies, function(S)
        lapply(names(l_partisanship[1:2]), function(PS)
          lapply(ps$parties, function(P) {
            df_temp <- df |> filter(strategy_2 == S, partisan %in% l_partisanship[[PS]], party == P)
            y <- df_temp[[v_outcomes[Y]]]
            if (nrow(df_temp) == 0 || all(is.na(y)) || length(unique(na.omit(y))) < 2) {
              print(paste("skipping ", paste(P, PS, S, Y, sep = "/"), " (NO ESTIMATION POSSIBLE: constant/NA DV)"))
              return(NULL)
            }
            run_feols_tidy(
              df = df_temp,
              outcome_var = v_outcomes[Y],
              extra_cols = list(
                outcome = Y,
                strategy = S,
                partisan = as.character(PS),
                party = P
              )
            )
          })
        ) |> bind_rows()) |> bind_rows()) |> bind_rows() |>
      mutate(outcome = factor(outcome, levels = unique(outcome)))

    wave_label <- ifelse(D == "wave_9", "Short-term Effects", "Long-term Effects")
    
    gg_f_IIc3b <- df_f_IIc3b |>
      gg_coefplot(aes(y = strategy, x = estimate, color = strategy)) +
      facet_nested(
        rows = vars(party, partisan),
        cols = vars(outcome),
        strip = strip_nested(
          text_y = list(
            element_text(angle = 90),
            element_text(angle = 0, hjust = 0)
          ),
          by_layer_y = TRUE
        )
      ) +
      labs(title = wave_label) +
      theme(
        panel.spacing.y = unit(0, "pt"),
        strip.background.y = element_rect(fill = "grey90", color = "black"),
        legend.position = "none"
      )

    print(gg_f_IIc3b)
    ggsave(
      filename = paste0(
        fig_dir, "/f_IIc3b", str_replace(OG, "main", ""), wave_suffix[[D]], ".pdf"
      ),
      plot = gg_f_IIc3b,
      width = 7,
      height = 8,
      device = cairo_pdf
    )
  }
}
```



## Appendix I: Attrition analysis

## Appendix J: Downstream effects on AfD support 


```{r}
#| label: analysis-maintained-support
#| results: asis
#| include: false
party_support <- list(
  lm_robust(afd10 ~ afd9 * Z9, data = individual_df),
  lm_robust(cdu10 ~ cdu9 * Z9, data = individual_df),
  lm_robust(linke10 ~ linke9 * Z9, data = individual_df)
  )

party_support |> texreg::htmlreg()

```

```{r}
#| label: analysis-party-support-arrows
# Calculate mean party support by treatment group for arrow plot
arrow_data <- individual_df |> 
  group_by(Z9) |> 
  summarize(
    afd_w9 = mean(afd9, na.rm = TRUE),
    afd_w10 = mean(afd10, na.rm = TRUE),
    cdu_w9 = mean(cdu9, na.rm = TRUE), 
    cdu_w10 = mean(cdu10, na.rm = TRUE),
    linke_w9 = mean(linke9, na.rm = TRUE),
    linke_w10 = mean(linke10, na.rm = TRUE),
    spd_w9 = mean(spd9, na.rm = TRUE),
    spd_w10 = mean(spd10, na.rm = TRUE),
    gruene_w9 = mean(gruene9, na.rm = TRUE),
    gruene_w10 = mean(gruene10, na.rm = TRUE),
    fdp_w9 = mean(fdp9, na.rm = TRUE),
    fdp_w10 = mean(fdp10, na.rm = TRUE),
    bsw_w9 = mean(bsw9, na.rm = TRUE),
    bsw_w10 = mean(bsw10, na.rm = TRUE)
  ) |> 
  mutate(treatment = ifelse(Z9 == 1, "Treatment", "Control"))

# Reshape to long format for plotting
arrow_long <- arrow_data |> 
  select(treatment, afd_w9, afd_w10, cdu_w9, cdu_w10, linke_w9, linke_w10, 
         spd_w9, spd_w10, gruene_w9, gruene_w10, fdp_w9, fdp_w10, bsw_w9, bsw_w10) |> 
  pivot_longer(cols = -treatment, names_to = "party_wave", values_to = "support") |> 
  separate(party_wave, into = c("party", "wave"), sep = "_w") |> 
  pivot_wider(names_from = wave, values_from = support, names_prefix = "w") |> 
  mutate(party = case_when(
    party == "afd" ~ "AfD",
    party == "cdu" ~ "CDU/CSU", 
    party == "linke" ~ "Linke",
    party == "spd" ~ "SPD",
    party == "gruene" ~ "Grüne",
    party == "fdp" ~ "FDP",
    party == "bsw" ~ "BSW"
  ))

# Create arrow plot
p_arrows <- ggplot(arrow_long, aes(x = w9, y = w10)) +
  geom_point(aes(color = treatment), size = 3, alpha = 0.7) +
  geom_segment(
    data = arrow_long |> 
      pivot_wider(names_from = treatment, values_from = c(w9, w10)) |> 
      filter(!is.na(w9_Control) & !is.na(w9_Treatment)),
    aes(x = w9_Control, y = w10_Control, 
        xend = w9_Treatment, yend = w10_Treatment),
    arrow = arrow(length = unit(0.2, "cm")), 
    color = "black", size = 1
  ) +
  geom_text_repel(
    aes(label = ifelse(treatment == "Control", party, "")),
    size = 3, force = 2, color = "black"
  ) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.5) +
  labs(
    x = "Party Support in Wave 9", 
    y = "Party Support in Wave 10",
    title = "Changes in Party Support: Control vs Treatment",
    subtitle = "Arrows show movement from Control to Treatment group means"
  ) +
  scale_color_manual(values = c("Control" = "#F8766D", "Treatment" = "#00BFC4")) +
  theme_bw() +
  theme(legend.title = element_blank())

print(p_arrows)

ggsave(
  filename = file.path(fig_dir, "party_support_arrows.pdf"),
  plot = p_arrows,
  device = cairo_pdf
)
```


```{r}
#| label: analysis-did-ci-plot

# Create DiD plot with confidence intervals using simple regressions
# Fit simple DiD regressions for each party (change in support)

party_codes =  c("afd", "cdu", "linke", "spd", "gruene", "fdp", "bsw")
names(party_codes) = c("AfD", "CDU/CSU", "Linke",   "SPD",  "Grüne",  "FDP",  "BSW")

# this model is ANOVA style; w10 conditioning on w9
# not using a change score

change_models <-
  party_codes |>
  lapply(function(party) {
    paste0(party, "10 ~ Z9 * ", party, "9_demean") |>
      as.formula() |>
      lm_robust(data = individual_df) |>
      tidy() } ) |>
  bind_rows(.id = "party") |>
  filter(term == "Z9")
      
# Create  plot with confidence intervals
plot_change <- function(
    results = change_models,
    subtitle = "Effect of treatment on long term support, conditional on initial support") {

  results   |>
  ggplot(aes(x = reorder(party, estimate), y = estimate)) +
  geom_col(aes(fill = ifelse(estimate > 0, "Positive", "Negative")), 
           alpha = 0.7, width = 0.6) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                width = 0.2, color = "black", size = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_text(aes(label = sprintf("%.3f\n(p=%.3f)", estimate, p.value)), 
            size = 2.8) +
  scale_fill_manual(values = c("Positive" = "#2E8B57", "Negative" = "#DC143C")) +
  labs(
    x = "Party",
    y = "Change in support (outcome on 0 to 1 scale)",
    title = "Treatment Effects (with 95% CI)",
    subtitle = subtitle,
    caption = "Error bars show 95% confidence intervals."
  ) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    plot.subtitle = element_text(size = 9),
    plot.caption = element_text(size = 8)
  ) +
  coord_flip()
}

changew9w10 <- plot_change(
  results = change_models,
  subtitle = "Effect of treatment on long term support, conditional on initial support")

print(changew9w10)

ggsave(
  filename = file.path(fig_dir, "party_support_did_ci.pdf"),
  plot = changew9w10,
  device = cairo_pdf
)

```


## short term political

```{r}
#| label: analysis-shortterm-plot

df_w9_ptv <- read_rds("data/df_w9_ptv.rds")

short_models <- 
  
  party_codes |> 
  lapply(function(party) {
    paste0("ptv_post_", party, " ~ workshop * ptv_pre_", party) |>
    as.formula() |>
    lm_robust(data = df_w9_ptv) |> 
    tidy()}
) |> bind_rows(.id = "party") |>
  filter(term == "workshop")

# Create  plot with confidence intervals
p_ci <- 
  changew9w10 <- plot_change(
  results = short_models,
  subtitle = "Effect of treatment on short term support, conditional on initial support")

  
print(p_ci)

ggsave(
  filename = file.path(fig_dir, "party_support_ptv_shortterm.pdf"),
  plot = p_ci,
  device = cairo_pdf
)

```





## Appendix K: Changes in Party Identification

```{r, eval = FALSE}
#| label: analysis-pid-change-overall

options(scipen = 999)  # discourage scientific notation

pid_overall <- build_pid_lodes(df)

fig_pid_change <- plot_pid_alluvial(
  lodes = pid_overall$lodes,
  party_cols = pid_overall$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change.pdf"),
  plot = fig_pid_change,
  device = cairo_pdf
)
```


## within treatment

```{r, eval = FALSE}
#| label: analysis-pid-change-treated

pid_treat <- build_pid_lodes(df |> filter(treated_w9 == 1))

fig_pid_change_treat <- plot_pid_alluvial(
  lodes = pid_treat$lodes,
  party_cols = pid_treat$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change_treat)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change_treat.pdf"),
  plot = fig_pid_change_treat,
  device = cairo_pdf
)
```

## within control

```{r, eval = FALSE}
#| label: analysis-pid-change-control

pid_control <- build_pid_lodes(df |> filter(treated_w9 == 0))

fig_pid_change_control <- plot_pid_alluvial(
  lodes = pid_control$lodes,
  party_cols = pid_control$party_cols,
  title_text = "Party identification transitions: Wave 9 \u2192 Wave 10"
)

print(fig_pid_change_control)
ggsave(
  filename = file.path(fig_dir, "fig_pid_change_control.pdf"),
  plot = fig_pid_change_control,
  device = cairo_pdf
)

```


## Appendix L: Correlations between short term and long term outcomes

Correlation structure among outcomes by treatment and wave. Ellipses indicate sign and strength; red/blue color encodes sign.

```{r}
#| label: analysis-outcome-correlations

# Compute correlations for both waves (within wave, by treatment)
cor_w9 <- build_cor_df(datasets$wave_9, "Short-term")
cor_w10 <- build_cor_df(datasets$wave_10, "Long-term")

cor_long <- bind_rows(cor_w9, cor_w10) |>
  mutate(sign = ifelse(r >= 0, "positive", "negative"))

# Prepare indices for grid positions
var_levels <- names(v_outcomes)
cor_long <- cor_long |>
  mutate(
    x_idx = match(var2, var_levels),
    y_idx = match(var1, var_levels)
  )

# Upper triangle: filled ellipses inside cells, scaled to avoid overlap
scale_in_cell <- 0.42
ellipse_upper <- cor_long |>
  filter(y_idx < x_idx) |>
  group_by(wave, treat, var1, var2, r, x_idx, y_idx, sign) |>
  do({
    rr <- .$r[1]
    S <- matrix(c(1, rr, rr, 1), nrow = 2)
    e <- as.data.frame(ellipse::ellipse(S, centre = c(0, 0), level = 0.68, npoints = 80))
    # normalize to unit box then scale to cell fraction
    maxabs <- max(max(abs(e$x)), max(abs(e$y)), 1e-9)
    e$x <- (e$x / maxabs) * scale_in_cell + .$x_idx[1]
    e$y <- (e$y / maxabs) * scale_in_cell + .$y_idx[1]
    e$wave <- .$wave[1]
    e$treat <- .$treat[1]
    e$var1 <- .$var1[1]
    e$var2 <- .$var2[1]
    e$sign <- .$sign[1]
    e$r <- rr
    e
  }) |>
  ungroup()

# Lower triangle: numeric labels
label_lower <- cor_long |>
  filter(y_idx > x_idx) |>
  mutate(label = sprintf("%.2f", r))

# Diagonal: blanks (or could set to 1.00 if desired)

p_cor <- ggplot() +
  geom_polygon(
    data = ellipse_upper,
    aes(x = x, y = y, group = interaction(wave, treat, var1, var2), fill = sign),
    color = NA, alpha = 0.75
  ) +
  geom_text(
    data = label_lower,
    aes(x = x_idx, y = y_idx, label = label, color = sign),
    size = 3
  ) +
  scale_fill_manual(values = c(positive = "#d73027", negative = "#4575b4"), name = "Sign") +
  scale_color_manual(values = c(positive = "#d73027", negative = "#4575b4"), guide = "none") +
  scale_x_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  scale_y_continuous(breaks = seq_along(var_levels), labels = var_levels, expand = expansion(mult = 0.05)) +
  coord_fixed() +
  labs(x = NULL, y = NULL) +
  theme_tiktok() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)
  ) +
  facet_grid(rows = vars(treat), cols = vars(wave))

print(p_cor)
ggsave(
  filename = file.path(
    fig_dir,
    paste0("correlation_ellipses.pdf")
  ),
  plot = p_cor,
  width = 9,
  height = 7,
  device = cairo_pdf
)
```


## Attrition

```{r}
#| label: analysis-attrition
#| message: false
#| warning: false
#| eval: false

results <- compute_attrition_results(
  data = df,
  covariates = covs,
  treat_col = "treated_w9",
  outcome = "attrit"
)

# Apply labels & ordering
res_plot <- na.omit(results)
res_plot <- res_plot[order(res_plot$estimate), ]
res_plot$label <- labels_en[res_plot$variable]
res_plot$label[is.na(res_plot$label)] <- res_plot$variable
res_plot$label <- factor(res_plot$label, levels = res_plot$label)

fig_attrit_interaction <- ggplot(res_plot, aes(x = estimate, y = label)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0) +
  geom_point() +
  labs(
    title = "Treatment \u00d7 Covariate Interactions on Attrition (LPM)",
    subtitle = "Points: interaction of treated with covariate; bars: 95% CI",
    x = "Interaction estimate (\u0394 probability of attrition)",
    y = NULL
  ) +
  theme_bw()

print(fig_attrit_interaction)
ggsave(
  filename = file.path(fig_dir, "fig_attrit_interaction.pdf"),
  plot = fig_attrit_interaction,
  device = cairo_pdf
)

```


## Comment classification


```{r ,message=FALSE,warning=FALSE}
comments_df <-read.csv("data/comment_classification.csv")


# Desired order
levels_vec <- c(
  "0 = setup skepticism",
  "1 = platform-focused",
  "2 = content-focused",
  "3 = other/unclear"
)

comments_plot <- comments_df %>%
  mutate(
    scale_label = fct_explicit_na(scale_label, na_level = "NA"),
    scale_label = fct_relevel(scale_label, levels_vec, after = 0) # keep 0–3 in order; "NA" (if present) goes last
  ) %>%
  count(scale_label, name = "n") %>%
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = scale_label, y = pct)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 0.1)),
            vjust = -0.25, size = 4) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    x = NULL, y = "Share of comments",
    title = "Comment classification (percentage of total)"
  ) +
  theme_bw(base_size = 13) +
  theme(panel.grid.major.x = element_blank())

comments_plot
ggsave('figs/fig_classification_comments.pdf', width = 8, height = 4)


```

