---
title: "Digital literacy: paper and SI analyses"
subtitle: Replication code for manuscript figures and SI Tables S3–S14 / Figures S2–S15
author: Kristina Aleksandrovna Pedersen, Ferdinand Geissler, Felix Hartmann, Johannes Giesecke, Macartan Humphreys, Heike Klüver
format:
  html:
    number-sections: true
    embed-resources: true
    code-fold: true
    toc: true
    include-in-header:
      text: |
        <style>
        figcaption .figure-number, caption .table-number { display: none; }
        </style>
        <script>
        document.addEventListener("DOMContentLoaded", function () {
          function stripAutoNum(el) {
            var html = el.innerHTML
              .replace(/^(Figure|Table)\s+\d+\s*:\s*/i, "")
              .replace(/^(\s|&nbsp;|\u00a0)*\d+(\s|&nbsp;|\u00a0)+(?=(Fig\.|Table ))/i, "");
            el.innerHTML = html;
          }
          document.querySelectorAll("figcaption, caption").forEach(stripAutoNum);
        });
        </script>
crossref:
  fig-title: ""
  tbl-title: ""
  title-delim: ""
execute:
  echo: true
  warning: true
  message: false
---

Not generated here (static SI inputs): **Table S1** video descriptives; **Table S2** scraped handles; **Fig. S1** example-video PNG; workshop/interface screenshots; **Table S15** PAP–manuscript reconciliation (inline in `PNAS_SI_revised.tex`). Compiled SI figure numbers follow TeX captions; PDF stems can differ (Fig. S4 is `fig_s3_by_strategy`, Fig. S5 is `fig_s4_type_treat_did`, Fig. S15 is `fig_s16_fig1_nofe`).

# Setup

```{r}
#| label: analysis-setup-packages

pacman::p_load(
  forcats,
  scales,
  fixest,
  tidyverse,
  estimatr,
  haven,
  knitr,
  broom,
  ellipse,
  ggrepel,
  texreg,
  ggalluvial,
  ggh4x
)
```


## Configuration

```{r}
#| label: analysis-configuration

setFixest_notes(FALSE)
pref_var <- "party_preference_"

strategies <- c("political\n(emotional)", "political\n(neutral)")

est_dir <- "ests"
gg_dir  <- "ggs"
fig_dir <- "figs"
tab_dir <- "tabs"
paper_root <- "../TikTok_PNAS"

v_outcomes <- c(
  "Like" = "videoLikep1r",
  "Share" = "videoSharep1r",
  "Bookmark" = "videoBookmarkp1r",
  "Report" = "videoCommentTickedp1r",
  "Watch Time" = "watch_percentage_",
  "Skip" = "skipped_video_"
)

l_outcomegroups <- list(
  main = c("Like", "Report", "Share", "Bookmark"),
  "_other" = c("Skip", "Watch Time")
)

# Paper-facing horizon labels (datasets remain wave_9 / wave_10)
horizon_wave_levels <- c("Wave 1", "Wave 2")

l_partisanship <- list(
  "Supporter: Yes" = 1,
  "Supporter: No" = 0,
  "All" = c(0, 1)
)

party_codes <- c("afd", "cdu", "linke", "spd", "gruene", "fdp", "bsw")
party_names <- c("AfD", "CDU/CSU", "Linke", "SPD", "Grüne", "FDP", "BSW")
names(party_codes) <- party_names
names(party_names) <- party_codes

texreg_stars <- c(0.01, 0.05, 0.10)

strategy_color_values <- c(
  "political\n(emotional)" = "black",
  "political\n(neutral)" = "grey55",
  "entertainment" = "grey55"
)
strategy_order_article <- c(
  "political\n(emotional)",
  "political\n(neutral)",
  "entertainment"
)
```


## Helper functions

```{r}
#| label: analysis-helper-functions

# Video FE, cluster by respondent ID.
run_feols_tidy <- function(df, outcome_var, extra_cols = list()) {
  feols(
    as.formula(paste(outcome_var, "~ workshop_Treatment | video")),
    data = df,
    cluster = ~ID
  ) |>
    tidy(conf.int = TRUE) |>
    bind_cols(as_tibble(extra_cols))
}

estimate_pooled_ates <- function(df, outcomes) {
  lapply(outcomes, function(Y) {
    lapply(unique(as.character(df$strategy_2)), function(S) {
      run_feols_tidy(
        df = df |> filter(strategy_2 == S),
        outcome_var = v_outcomes[[Y]],
        extra_cols = list(outcome = Y, strategy = S)
      )
    }) |> bind_rows()
  }) |> bind_rows()
}

outcome_super <- function(outcome) {
  factor(
    if_else(as.character(outcome) %in% l_outcomegroups$main, "Engagement", "Attention"),
    levels = c("Engagement", "Attention")
  )
}

# 6-column figures: Like/Report/Share/Bookmark/Skip share one x-range
# (estimates + CIs); Watch Time uses its own. Unnamed list matches nested
# columns left-to-right in `outcomes` order.
shared_binary_x_scales <- function(df, outcomes) {
  watch <- "Watch Time"
  shared <- setdiff(as.character(outcomes), watch)
  rng <- function(ok) {
    dat <- df |> filter(as.character(outcome) %in% ok)
    vals <- dat$estimate
    if ("conf.low" %in% names(dat)) {
      vals <- c(vals, dat$conf.low, dat$conf.high)
    }
    range(vals, na.rm = TRUE)
  }
  shared_lim <- rng(shared)
  watch_lim <- rng(watch)
  lapply(as.character(outcomes), function(y) {
    scale_x_continuous(limits = if (identical(y, watch)) watch_lim else shared_lim)
  })
}

plot_pooled_horizon <- function(estimates, outcomes, title, subtitle) {
  estimates |>
    mutate(
      horizon = factor(horizon, levels = horizon_wave_levels),
      strategy = factor(as.character(strategy), levels = rev(strategy_order_article)),
      outcome = factor(outcome, levels = outcomes),
      strat_color = as.character(strategy)
    ) |>
    ggplot(aes(x = estimate, y = strategy, color = strat_color)) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
    geom_point(size = 1.8) +
    facet_grid(rows = vars(horizon), cols = vars(outcome)) +
    scale_color_manual(values = strategy_color_values, guide = "none") +
    labs(x = "Average treatment effect", y = NULL, title = title, subtitle = subtitle) +
    theme_bw(base_size = 10) +
    theme(
      axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
      axis.text.y = element_text(size = 9),
      strip.text = element_text(size = 10),
      panel.spacing.y = unit(6, "pt")
    )
}

replace_file <- function(from, to) {
  if (file.exists(to) && unlink(to) != 0) {
    file.rename(to, paste0(to, ".old"))
  }
  if (!isTRUE(file.rename(from, to))) {
    file.copy(from, to, overwrite = TRUE)
    unlink(from)
  }
}

# Persist tidy/glance only; full fixest lists store scores/residuals/FE vectors.
tidy_fixest_tree <- function(x) {
  if (inherits(x, "fixest")) {
    list(tidy = broom::tidy(x, conf.int = TRUE), glance = broom::glance(x))
  } else if (is.list(x)) {
    lapply(x, tidy_fixest_tree)
  } else {
    x
  }
}

write_tab_rds <- function(models, dest_stem) {
  path <- file.path(est_dir, paste0(dest_stem, ".rds"))
  tmp <- file.path(dirname(path), paste0(".", basename(path), ".tmp"))
  write_rds(tidy_fixest_tree(models), tmp)
  replace_file(tmp, path)
}

write_fig <- function(stem, estimates, plot, width = NA, height = NA, publish = NULL) {
  est_path <- file.path(est_dir, paste0(stem, ".rds"))
  gg_path  <- file.path(gg_dir, paste0(stem, ".rds"))
  pdf_path <- file.path(fig_dir, paste0(stem, ".pdf"))
  tmp_near <- function(path) file.path(dirname(path), paste0(".", basename(path), ".tmp"))
  write_rds(estimates, tmp_near(est_path))
  replace_file(tmp_near(est_path), est_path)
  write_rds(plot, tmp_near(gg_path))
  replace_file(tmp_near(gg_path), gg_path)
  tmp_pdf <- tmp_near(pdf_path)
  save_pdf <- function(dev) {
    if (is.na(width) && is.na(height)) {
      ggsave(tmp_pdf, plot, device = dev)
    } else {
      ggsave(tmp_pdf, plot, device = dev, width = width, height = height)
    }
  }
  tryCatch(save_pdf(cairo_pdf), error = function(e) save_pdf(pdf))
  replace_file(tmp_pdf, pdf_path)
  if (!is.null(publish)) {
    file.copy(pdf_path, publish, overwrite = TRUE)
  }
  print(plot)
}

paper_pdf <- function(stem) file.path(paper_root, "figs", paste0(stem, ".pdf"))
si_pdf <- function(stem) file.path(paper_root, "sn-figs", paste0(stem, ".pdf"))

publish_tex <- function(stem) {
  dest <- file.path(paper_root, "sn-tables", paste0(stem, ".tex"))
  file.copy(file.path(tab_dir, paste0(stem, ".tex")), dest, overwrite = TRUE)
}
```



# Data 

```{r}
#| label: data-imports

datasets <- list(
  wave_9  = read_rds("data/wave_9.rds"),
  wave_10 = read_rds("data/wave_10.rds"))

sample_overview <- read_rds("data/sample_overview.rds")

df_w10_no_repeated_videos <- datasets$wave_10 |>
  filter(shown_both_waves == 0)

tibble(
  sample = c("Original Wave 2", "No repeated videos"),
  observations = c(
    nrow(datasets$wave_10),
    nrow(df_w10_no_repeated_videos)
  ),
  respondents = c(
    n_distinct(datasets$wave_10$ID),
    n_distinct(df_w10_no_repeated_videos$ID)
  )
)


df_w9_w10  <- read_rds("data/df_w9_w10.rds")|>
  mutate(citysize = as.numeric(citysize))

comments_df <-read.csv("data/comment_classification.csv")

# covariates

# ---- English labels for covariates (matches prepared data after tolower) ----
labels_en <- c(
  # Basics
  alter         = "Age",
  gender_female = "Female (vs male)",
  citysize      = "City size",

  # Region binaries and state indicators
  east = "East (vs West)",
  state_baden_wuerttemberg    = "State: Baden-Württemberg",
  state_bayern                = "State: Bavaria",
  state_berlin                = "State: Berlin",
  state_brandenburg           = "State: Brandenburg",
  state_bremen                = "State: Bremen",
  state_hamburg               = "State: Hamburg",
  state_hessen                = "State: Hesse",
  state_mecklenburg_vorpommern = "State: Mecklenburg–Western Pomerania",
  state_niedersachsen         = "State: Lower Saxony",
  state_nordrhein_westfalen   = "State: North Rhine-Westphalia",
  state_rheinland_pfalz       = "State: Rhineland-Palatinate",
  state_saarland              = "State: Saarland",
  state_sachsen               = "State: Saxony",
  state_sachsen_anhalt        = "State: Saxony-Anhalt",
  state_schleswig_holstein    = "State: Schleswig-Holstein",
  state_thueringen            = "State: Thuringia",

  # Urbanization indicators
  urban_ballungsraum  = "Urban: metropolitan area",
  urban_stadtregion   = "Urban: city region",
  urban_mittelzentrum = "Urban: medium-sized center",
  urban_high          = "High urbanization",

  # Social-media use
  video_userfacebook       = "Uses Facebook",
  video_usertiktok         = "Uses TikTok",
  video_usersnapchat       = "Uses Snapchat",
  video_userpinterest      = "Uses Pinterest",
  video_userx_ehem_twitter = "Uses X/Twitter",
  video_usertwitch         = "Uses Twitch",

  # Political attitudes
  politikinteresse = "Political interest",
  lr               = "Left–right ideology",

  # Party regarded as competent
  competence_cdu_csu = "Competent party: CDU/CSU",
  competence_spd     = "Competent party: SPD",
  competence_afd     = "Competent party: AfD",
  competence_greens  = "Competent party: Greens",
  competence_fdp     = "Competent party: FDP",
  competence_left    = "Competent party: The Left",
  competence_bsw     = "Competent party: BSW",

  # Party identification at wave 9
  party_id_w9_cdu    = "Party ID: CDU/CSU",
  party_id_w9_spd    = "Party ID: SPD",
  party_id_w9_afd    = "Party ID: AfD",
  party_id_w9_gruene = "Party ID: Greens",
  party_id_w9_fdp    = "Party ID: FDP",
  party_id_w9_linke  = "Party ID: The Left",
  party_id_w9_bsw    = "Party ID: BSW",

  # Pre-treatment propensities to vote
  ptv_w9_pre_cdu    = "PTV CDU/CSU (pre)",
  ptv_w9_pre_spd    = "PTV SPD (pre)",
  ptv_w9_pre_linke  = "PTV The Left (pre)",
  ptv_w9_pre_gruene = "PTV Greens (pre)",
  ptv_w9_pre_fdp    = "PTV FDP (pre)",
  ptv_w9_pre_afd    = "PTV AfD (pre)",
  ptv_w9_pre_bsw    = "PTV BSW (pre)",

  # Other attitudes
  prior_performance_general_2 = "Government performance (prior)",
  solidaritat                 = "Solidarity",
  sozialer_zusammenhalt       = "Social cohesion",
  migration                   = "Immigration attitudes",

  # TikTok-specific indicators
  tiktok_user_yes      = "Current TikTok user",
  tiktok_user_no       = "Not a TikTok user",
  tiktok_potential_yes = "Open to getting a TikTok account",
  tiktok_potential_no  = "Not open to getting a TikTok account",

  # Employment status
  employment_fulltime         = "Employment: full-time",
  employment_parttime         = "Employment: part-time",
  employment_marginal         = "Employment: marginal/irregular",
  employment_training_service = "Employment: training/service",
  employment_not_working      = "Not currently employed",

  # Occupational position
  occupation_worker         = "Occupation: worker",
  occupation_employee       = "Occupation: employee",
  occupation_public_service = "Occupation: public service",
  occupation_self_employed  = "Occupation: self-employed",

  # Education
  school_education_level = "School education level",
  vocational_basic       = "Vocational education: basic",
  vocational_advanced    = "Vocational education: advanced",
  vocational_other       = "Vocational education: other",
  vocational_none        = "No vocational qualification",

  # Household and demographic characteristics
  eigene_kinder                 = "Has children",
  haushaltsgrobe                = "Household size",
  migrationshintergrund_eltern  = "Parental migration background",
  haushaltseinkommen            = "Household income"
)

```



# Paper

Exhibits in manuscript order. Each item has an analysis chunk (estimates) and a formatting chunk (figure/table).

## Sample Overview
```{r}
#| label: tab-sample-overview
#| results: 'asis'

sample_table <- sample_overview |>
  mutate(wave = if_else(duplicated(wave), "", wave)) |>
  select(
    Wave = wave,
    `Sample stage` = sample_stage,
    Respondents = respondents,
    `Role in analysis` = analysis_role
  )

sample_tex <- knitr::kable(
  sample_table,
  format = "latex",
  booktabs = TRUE,
  digits = 0,
  format.args = list(big.mark = ","),
  caption = "Sample construction by study wave.",
  label = "tab:sample-overview",
  align = c("l", "l", "r", "l")
)

writeLines(
  sample_tex,
  file.path(tab_dir, "tab_sample_overview.tex")
)

knitr::kable(
  sample_table,
  digits = 0,
  format.args = list(big.mark = ","),
  caption = "Sample construction by study wave"
)

```



## Fig. 1. Effects of the digital literacy workshop on engagement with TikTok-style videos.

Pooled Wave 1 and Wave 2 ATEs on like, report, share, bookmark, skip, and watch time, by content type. Video FE; SEs clustered by respondent. Super-columns: Engagement (first four) and Attention (skip, watch time). Stem: `fig_1_engagement`.

```{r}
#| label: fig-1-analysis

fig1_outcomes <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])

estimates_fig1 <- bind_rows(
  estimate_pooled_ates(datasets$wave_9, fig1_outcomes) |>
    mutate(horizon = "Wave 1"),
  estimate_pooled_ates(datasets$wave_10, fig1_outcomes) |>
    mutate(horizon = "Wave 2")
)
```

```{r}
#| label: fig-1-format
#| fig-width: 12
#| fig-height: 5
#| fig-cap: "Fig. 1. Effects of the digital literacy workshop on engagement with TikTok-style videos."

fig1 <- estimates_fig1 |>
  mutate(
    horizon = factor(horizon, levels = horizon_wave_levels),
    strategy = factor(as.character(strategy), levels = rev(strategy_order_article)),
    outcome = factor(outcome, levels = fig1_outcomes),
    super = outcome_super(outcome),
    strat_color = as.character(strategy)
  ) |>
  ggplot(aes(x = estimate, y = strategy, color = strat_color)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(horizon ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = shared_binary_x_scales(estimates_fig1, fig1_outcomes)) +
  scale_color_manual(values = strategy_color_values, guide = "none") +
  labs(
    x = "Average treatment effect",
    y = NULL,
    title = "Treatment effects by content type",
    subtitle = "Video FE; SEs clustered by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10),
    panel.spacing.y = unit(6, "pt")
  )

write_fig(
  stem = "fig_1_engagement",
  estimates = estimates_fig1,
  plot = fig1,
  width = 12,
  height = 5,
  publish = paper_pdf("fig_1_engagement")
)
```

## Fig. 2. By party and partisanship.

Conditional effects by party and sample. Emotionally manipulative political videos, Wave 1; everyone, partisans, and non-partisans. Super-columns: Engagement (like, report, share, bookmark) and Attention (skip, watch time). Stem: `fig_2_party_partisanship`.

```{r}
#| label: fig-2-analysis
#| fig-width: 12
#| fig-height: 8

# Demeaned party dummies, video FE, cluster ID.
# Bare treatment = all-parties ATE; party rows recover party-specific TEs.
fit_lin_party_feols <- function(df, outcome_var, party_levels, party_code_map,
                                ref_party = party_levels[length(party_levels)]) {
  interact_parties <- setdiff(party_levels, ref_party)
  df_m <- df |>
    filter(!is.na(.data[[outcome_var]]), !is.na(party), party %in% party_levels) |>
    mutate(party = factor(party, levels = party_levels))

  pi <- setNames(numeric(length(interact_parties)), interact_parties)
  for (p in interact_parties) {
    raw <- as.integer(df_m$party == p)
    pi[p] <- mean(raw, na.rm = TRUE)
    df_m[[paste0("pdm_", party_code_map[[p]])]] <- raw - pi[p]
  }

  pdm_terms <- paste0("pdm_", party_code_map[interact_parties])
  rhs <- paste0("workshop_Treatment * (", paste(pdm_terms, collapse = " + "), ")")
  fit <- feols(
    as.formula(paste(outcome_var, "~", rhs, "| video")),
    data = df_m,
    cluster = ~ID
  )

  b <- coef(fit)
  V <- vcov(fit)
  treat <- "workshop_Treatment"
  lincom <- function(cvec) {
    cvec <- cvec[names(b)]
    cvec[is.na(cvec)] <- 0
    est <- sum(cvec * b)
    se <- sqrt(as.numeric(t(cvec) %*% V %*% cvec))
    tibble(
      estimate = est,
      std.error = se,
      conf.low = est - 1.96 * se,
      conf.high = est + 1.96 * se,
      p.value = 2 * pnorm(-abs(est / se))
    )
  }

  c_ate <- setNames(rep(0, length(b)), names(b))
  c_ate[treat] <- 1
  out_ate <- lincom(c_ate) |> mutate(term = treat, party = "All parties")

  out_parties <- lapply(party_levels, function(p) {
    cvec <- setNames(rep(0, length(b)), names(b))
    cvec[treat] <- 1
    for (j in interact_parties) {
      nm <- paste0(treat, ":pdm_", party_code_map[[j]])
      if (!nm %in% names(b)) next
      cvec[nm] <- if (identical(p, j)) 1 - pi[j] else -pi[j]
    }
    lincom(cvec) |> mutate(term = paste0("TE_", party_code_map[[p]]), party = p)
  }) |> bind_rows()

  bind_rows(out_ate, out_parties) |> mutate(outcome_var = outcome_var)
}

fig2_samples <- list("All" = NULL, "Partisan" = 1L, "Non-partisan" = 0L)
fig2_sample_order <- names(fig2_samples)
fig2_sample_dodge_levels <- rev(fig2_sample_order)
party_labels_az <- sort(names(party_codes))
party_row_levels <- c("All parties", party_labels_az)

fig2_outcomes <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])

df_fig2 <- datasets$wave_9 |>
  filter(strategy_2 == strategies[1], !is.na(party), party %in% names(party_codes))

estimates_fig2 <- lapply(fig2_sample_order, function(samp) {
  df_s <- df_fig2
  if (!is.null(fig2_samples[[samp]])) {
    df_s <- df_s |> filter(partisan == fig2_samples[[samp]])
  }
  lapply(fig2_outcomes, function(Y) {
    fit_lin_party_feols(
      df = df_s,
      outcome_var = v_outcomes[[Y]],
      party_levels = party_labels_az,
      party_code_map = party_codes
    ) |>
      mutate(outcome = Y, sample = samp)
  }) |>
    bind_rows()
}) |>
  bind_rows() |>
  mutate(
    outcome = factor(outcome, levels = fig2_outcomes),
    sample = factor(sample, levels = fig2_sample_dodge_levels),
    party = factor(party, levels = party_row_levels)
  )
```

```{r}
#| label: fig-2-format
#| fig-width: 12
#| fig-height: 8
#| fig-cap: "Fig. 2. By party and partisanship."

dodge_fig2 <- position_dodge(width = 0.55)

# Per-outcome x-limits from point estimates only (not CIs). Buffer is 15% of
# that panel's estimate range, with a 0.005 floor when the range is tiny.
# facetted_pos_scales clips OOB geoms (wide error bars) like coord_cartesian;
# ggh4x ignores per-scale oob, so rows are not dropped.
fig2_x_lims <- estimates_fig2 |>
  summarise(
    lo = min(estimate, na.rm = TRUE),
    hi = max(estimate, na.rm = TRUE),
    .by = outcome
  ) |>
  mutate(
    pad = pmax(0.15 * (hi - lo), 0.005),
    xmin = lo - pad,
    xmax = hi + pad
  )

# Unnamed list matches nested columns left-to-right (fig2_outcomes order).
fig2_x_scales <- lapply(fig2_outcomes, function(y) {
  r <- fig2_x_lims[as.character(fig2_x_lims$outcome) == y, ]
  scale_x_continuous(
    limits = c(r$xmin, r$xmax),
    expand = expansion(mult = 0)
  )
})

fig2 <- estimates_fig2 |>
  mutate(
    super = outcome_super(outcome)
  ) |>
  ggplot(aes(x = estimate, y = party, color = sample)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    width = 0.2,
    position = dodge_fig2
  ) +
  geom_point(size = 1.6, position = dodge_fig2) +
  facet_nested(. ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = fig2_x_scales) +
  scale_y_discrete(limits = rev(party_row_levels)) +
  scale_color_discrete(
    limits = fig2_sample_dodge_levels,
    breaks = fig2_sample_order,
    guide = guide_legend(reverse = TRUE)
  ) +
  labs(
    x = "Average treatment effect",
    y = NULL,
    color = NULL,
    title = "Conditional effects by party and sample",
    subtitle = "Video FE; SEs clustered by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10)
  )

write_fig(
  stem = "fig_2_party_partisanship",
  estimates = estimates_fig2,
  plot = fig2,
  width = 12,
  height = 8,
  publish = paper_pdf("fig_2_party_partisanship")
)
```

# Supporting Information

Exhibits in compiled SI order. HTML figure labels start at **Fig. S2** (Fig. S1 is the static example-video PNG). Not created here: Table S1 (descriptives fragment), Table S2 (scraped-handle longtable), Fig. S1 (example-video PNG), workshop/interface screenshots, and Table S15 (PAP reconciliation, written in the SI `.tex`).

## Table S3. Average Cohen's Kappa between coder pairings

Mean pairwise Cohen's $\kappa$ across three coder rounds (anger, fear, superiority, and any-emotion vs none). Same statistic as `pre_survey_prep/3.3_Validted Political Set.ipynb`. Recomputed if `data/coder_ratings.rds` is present (wide panel with `anger_1`/`anger_2`/`anger_3`, and the same for fear and superiority); otherwise the published means from that notebook are written so this file still produces the SI `.tex`.

```{r}
#| label: tab-s3-analysis

cohen_kappa <- function(x, y) {
  ok <- stats::complete.cases(x, y)
  x <- as.integer(x[ok])
  y <- as.integer(y[ok])
  if (length(x) < 2L) return(NA_real_)
  p0 <- mean(x == y)
  px <- c(mean(x == 0), mean(x == 1))
  py <- c(mean(y == 0), mean(y == 1))
  pe <- sum(px * py)
  if (abs(1 - pe) < 1e-12) return(NA_real_)
  unname((p0 - pe) / (1 - pe))
}
mean_pairwise_kappa <- function(c1, c2, c3) {
  mean(c(cohen_kappa(c1, c2), cohen_kappa(c1, c3), cohen_kappa(c2, c3)), na.rm = TRUE)
}

coder_path <- "data/coder_ratings.rds"
kappa_src <- "pre_survey_prep/3.3_Validted Political Set.ipynb (published means)"
kappa_s3 <- c(
  anger = 0.492,
  fear = 0.453,
  superiority = 0.371,
  any_emotion = 0.404
)

if (file.exists(coder_path)) {
  cr <- read_rds(coder_path)
  need <- c(
    "anger_1", "anger_2", "anger_3",
    "fear_1", "fear_2", "fear_3",
    "superiority_1", "superiority_2", "superiority_3"
  )
  stopifnot(all(need %in% names(cr)))
  any_em <- function(a, f, s) {
    ifelse(
      a == 1 | f == 1 | s == 1,
      1L,
      ifelse(a == 0 & f == 0 & s == 0, 0L, NA_integer_)
    )
  }
  kappa_s3 <- c(
    anger = mean_pairwise_kappa(cr$anger_1, cr$anger_2, cr$anger_3),
    fear = mean_pairwise_kappa(cr$fear_1, cr$fear_2, cr$fear_3),
    superiority = mean_pairwise_kappa(
      cr$superiority_1, cr$superiority_2, cr$superiority_3
    ),
    any_emotion = mean_pairwise_kappa(
      any_em(cr$anger_1, cr$fear_1, cr$superiority_1),
      any_em(cr$anger_2, cr$fear_2, cr$superiority_2),
      any_em(cr$anger_3, cr$fear_3, cr$superiority_3)
    )
  )
  kappa_src <- coder_path
}
cat("Table S3 kappas from ", kappa_src, "\n", sep = "")
print(round(kappa_s3, 3))
```

```{r}
#| label: tab-s3-format
#| results: 'asis'

tex_s3 <- c(
  "\\begin{table}[ht]",
  "    \\centering",
  "\\begin{tabular}{|r|r|r|r|}",
  "\\hline",
  "\\textbf{Anger} & \\textbf{Fear} & \\textbf{Superiority} & \\textbf{Any emotion} \\\\",
  "\\hline",
  sprintf(
    "%.3f & %.3f & %.3f & %.3f \\\\",
    kappa_s3[["anger"]],
    kappa_s3[["fear"]],
    kappa_s3[["superiority"]],
    kappa_s3[["any_emotion"]]
  ),
  "\\hline",
  "\\end{tabular}",
  "    \\caption{Average Cohen's Kappa between coder pairings}",
  "    \\label{tab:cohens_kappa}",
  "\\end{table}"
)
writeLines(tex_s3, file.path(tab_dir, "tab_s3_cohens_kappa.tex"))
publish_tex("tab_s3_cohens_kappa")
knitr::kable(
  tibble(
    Anger = round(kappa_s3[["anger"]], 3),
    Fear = round(kappa_s3[["fear"]], 3),
    Superiority = round(kappa_s3[["superiority"]], 3),
    `Any emotion` = round(kappa_s3[["any_emotion"]], 3)
  ),
  caption = "Table S3. Average Cohen's Kappa between coder pairings"
)
```

## Table S4. Distribution of emotion categories in the full political sample and survey video bundle

Compiled SI Table S4 is `tab_s4_strategy_by_party_combined` (static TeX fragment). This chunk writes experiment-sample party × strategy counts (`tab_s4_strategy_by_party`). Party × `strategy_2` counts for the 400 experiment videos (unique `video` in Wave 1). Entertainment videos have blank party and form their own row; political videos are emotional or neutral.

```{r}
#| label: tab-s4-analysis

party_levels_s4 <- c("AfD", "BSW", "CDU/CSU", "FDP", "Grüne", "Linke", "SPD")

s4_vids <- datasets$wave_9 |>
  distinct(video, .keep_all = TRUE) |>
  mutate(
    row_lab = ifelse(strategy_2 == "entertainment", "Entertainment", as.character(party)),
    col_lab = case_when(
      strategy_2 == strategies[1] ~ "emotional",
      strategy_2 == strategies[2] ~ "neutral",
      strategy_2 == "entertainment" ~ "entertainment"
    )
  )
stopifnot(nrow(s4_vids) == 400L)

s4_tab <- as.data.frame.matrix(with(s4_vids, table(row_lab, col_lab))) |>
  tibble::rownames_to_column("row_lab") |>
  transmute(
    row_lab = factor(row_lab, levels = c(party_levels_s4, "Entertainment")),
    emotional,
    neutral,
    entertainment,
    all = emotional + neutral + entertainment
  ) |>
  arrange(row_lab)
s4_tab <- bind_rows(
  s4_tab,
  summarise(s4_tab, row_lab = "Total", across(-row_lab, sum))
)
```

```{r}
#| label: tab-s4-format
#| results: 'asis'

fmt_s4 <- function(r) {
  sprintf(
    "%s & %s & %s & %s & %s \\\\",
    r$row_lab, r$emotional, r$neutral, r$entertainment, r$all
  )
}
body <- vapply(seq_len(nrow(s4_tab)), function(i) {
  paste0(fmt_s4(s4_tab[i, ]), " \\hline")
}, character(1))
tex_s4 <- c(
  "\\begin{table}[ht]",
  "\\centering",
  "\\begin{tabular}{|l|l|l|l|l|}",
  "\\hline",
  " & \\textbf{Emotional political} & \\textbf{Neutral political} & \\textbf{Entertainment} & \\textbf{All} \\\\ \\hline",
  body,
  "\\end{tabular}",
  "\\caption{Strategy distribution across videos}",
  "\\label{tiktok:strategy}",
  "\\end{table}"
)
writeLines(tex_s4, file.path(tab_dir, "tab_s4_strategy_by_party.tex"))
publish_tex("tab_s4_strategy_by_party")
knitr::kable(
  s4_tab |>
    select(
      Party = row_lab,
      `Emotional political` = emotional,
      `Neutral political` = neutral,
      Entertainment = entertainment,
      All = all
    ),
  caption = "Table S4. Strategy distribution across videos (experiment sample; compiled SI Table S4 uses the combined fragment)"
)
```

## Fig. S2. Engagement with the platform.

Stem: `fig_s2_platform_comments`. Comment classification of open-ended platform remarks (ecological validity).

```{r}
#| label: fig-s2-analysis
#| message: false
#| warning: false

levels_vec <- c(
  "0 = setup skepticism",
  "1 = platform-focused",
  "2 = content-focused",
  "3 = other/unclear"
)
comments_counts <- comments_df |>
  mutate(
    scale_label = fct_explicit_na(scale_label, na_level = "NA"),
    scale_label = fct_relevel(scale_label, levels_vec, after = 0)
  ) |>
  count(scale_label, name = "n") |>
  mutate(pct = n / sum(n))
```

```{r}
#| label: fig-s2-format
#| fig-width: 8
#| fig-height: 4
#| fig-cap: "Fig. S2. Engagement with the platform."

fig_s2 <- comments_counts |>
  ggplot(aes(x = scale_label, y = pct)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 0.1)), vjust = -0.25, size = 4) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = "Share of comments", title = "Comment classification") +
  theme_bw(base_size = 13) +
  theme(panel.grid.major.x = element_blank())

write_fig(
  stem = "fig_s2_platform_comments",
  estimates = comments_counts,
  plot = fig_s2,
  width = 8,
  height = 4,
  publish = si_pdf("fig_s2_platform_comments")
)
```

## Fig. S3. Levels of outcomes by treatment condition.

Stem: `fig_s3_outcome_levels_treat_control`. Table-order companion to manuscript Figure 1: mean Wave 1 and Wave 2 outcome levels by content type and treatment (not ATEs). Same 2×6 layout; all three content types; cluster-robust 95% CIs by respondent. Super-columns: Engagement (first four) and Attention (skip, watch time). Each outcome column has its own x-scale.

```{r}
#| label: fig-s3-outcome-levels-analysis

treat_cols <- c(Control = "#4C78A8", Treatment = "#E45756")
outcome_order_levels <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])

df_levels_row <- bind_rows(
  datasets$wave_9 |> mutate(horizon = "Wave 1"),
  datasets$wave_10 |> mutate(horizon = "Wave 2")
) |>
  transmute(
    ID = as.character(ID),
    horizon = factor(horizon, levels = horizon_wave_levels),
    strategy = factor(as.character(strategy_2), levels = rev(strategy_order_article)),
    treatment = factor(
      ifelse(workshop_Treatment == 1, "Treatment", "Control"),
      levels = c("Control", "Treatment")
    ),
    Like = as.numeric(videoLikep1r),
    Report = as.numeric(videoCommentTickedp1r),
    Share = as.numeric(videoSharep1r),
    Bookmark = as.numeric(videoBookmarkp1r),
    Skip = as.numeric(skipped_video_),
    `Watch Time` = as.numeric(watch_percentage_)
  ) |>
  pivot_longer(
    cols = all_of(outcome_order_levels),
    names_to = "outcome",
    values_to = "y"
  ) |>
  filter(is.finite(y), !is.na(strategy), !is.na(treatment))

est_levels <- df_levels_row |>
  mutate(outcome = factor(outcome, levels = outcome_order_levels)) |>
  group_by(horizon, outcome, strategy, treatment) |>
  group_modify(~ {
    m <- estimatr::lm_robust(y ~ 1, data = .x, clusters = ID)
    broom::tidy(m, conf.int = TRUE) |>
      dplyr::filter(term == "(Intercept)") |>
      dplyr::transmute(
        estimate,
        std.error,
        conf.low,
        conf.high,
        n = nrow(.x),
        n_id = dplyr::n_distinct(.x$ID)
      )
  }) |>
  ungroup()
```

```{r}
#| label: fig-s3-outcome-levels-format
#| fig-width: 12
#| fig-height: 5.5
#| fig-cap: "Fig. S3. Levels of outcomes by treatment condition."

pd <- position_dodge(width = 0.5)

fig_s3_outcome_levels_treat_control <- est_levels |>
  mutate(super = outcome_super(outcome)) |>
  ggplot(aes(x = estimate, y = strategy, color = treatment)) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    width = 0.2,
    position = pd
  ) +
  geom_point(size = 1.8, position = pd) +
  facet_nested(horizon ~ super + outcome, scales = "free_x") +
  scale_color_manual(values = treat_cols, name = NULL) +
  labs(
    x = "Mean outcome level",
    y = NULL,
    title = "Outcome levels by content type and treatment",
    subtitle = "Video–respondent rows; cluster-robust 95% CIs by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10),
    panel.spacing.y = unit(6, "pt"),
    legend.position = "bottom"
  )

write_fig(
  stem = "fig_s3_outcome_levels_treat_control",
  estimates = est_levels,
  plot = fig_s3_outcome_levels_treat_control,
  width = 12,
  height = 5.5,
  publish = si_pdf("fig_s3_outcome_levels_treat_control")
)
```

## Fig. S4. Patterns conditional on strategy.

Stem: `fig_s3_by_strategy` (filename retained; compiled SI number is S4). Wave 1 ATEs by emotional strategy (anger, fear, superiority) on like, report, share, bookmark, skip, and watch time. Video FE; SEs clustered by respondent. Super-columns: Engagement (first four) and Attention (skip, watch time).

```{r}
#| label: fig-s3-by-strategy-analysis

s3_outcomes <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])
emotion_strats <- c("anger", "fear", "superiority")

estimates_s3 <- lapply(s3_outcomes, function(Y) {
  lapply(emotion_strats, function(S) {
    run_feols_tidy(
      df = datasets$wave_9 |> filter(strategy == S),
      outcome_var = v_outcomes[[Y]],
      extra_cols = list(outcome = Y, strategy = S)
    )
  }) |> bind_rows()
}) |>
  bind_rows() |>
  mutate(outcome = factor(outcome, levels = s3_outcomes))
```

```{r}
#| label: fig-s3-by-strategy-format
#| fig-width: 12
#| fig-height: 3.5
#| fig-cap: "Fig. S4. Patterns conditional on strategy."

fig_s3 <- estimates_s3 |>
  mutate(
    strategy = factor(as.character(strategy), levels = rev(emotion_strats)),
    outcome = factor(outcome, levels = s3_outcomes),
    super = outcome_super(outcome)
  ) |>
  ggplot(aes(x = estimate, y = strategy, color = strategy)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(. ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = shared_binary_x_scales(estimates_s3, s3_outcomes)) +
  scale_color_discrete(guide = "none") +
  labs(
    x = "Average treatment effect",
    y = NULL,
    title = "Wave 1 effects by emotional strategy",
    subtitle = "Video FE; SEs clustered by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10)
  )

write_fig(
  stem = "fig_s3_by_strategy",
  estimates = estimates_s3,
  plot = fig_s3,
  width = 12,
  height = 3.5,
  publish = si_pdf("fig_s3_by_strategy")
)
```

## Fig. S5. Differential effects for emotional political videos.

Stem: `fig_s4_type_treat_did` (filename retained; compiled SI number is S5). Treatment × type interactions on all six outcomes (emotional vs politically neutral; emotional vs entertainment). Pairwise samples; video FE; cluster-robust 95% CIs by respondent. Companion to Tables S5–S8. Super-columns: Engagement (first four) and Attention (skip, watch time).

```{r}
#| label: fig-s4-analysis

outcome_order_did <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])

contrast_specs <- list(
  "Emotional vs neutral\n× treatment" = strategies,
  "Emotional vs entertainment\n× treatment" = c(strategies[1], "entertainment")
)
horizon_data <- list(
  "Wave 1" = datasets$wave_9,
  "Wave 2" = datasets$wave_10
)

est_did <- bind_rows(lapply(names(horizon_data), function(h) {
  bind_rows(lapply(names(contrast_specs), function(c_lab) {
    df <- horizon_data[[h]] |>
      filter(strategy_2 %in% contrast_specs[[c_lab]]) |>
      mutate(
        type_dummy = as.integer(strategy_2 == strategies[1]),
        across(all_of(unname(v_outcomes)), \(z) as.numeric(haven::zap_labels(z)))
      )
    bind_rows(lapply(outcome_order_did, function(Y) {
      feols(
        as.formula(paste0(v_outcomes[[Y]], " ~ workshop_Treatment * type_dummy | video")),
        data = df,
        cluster = ~ID
      ) |>
        broom::tidy(conf.int = TRUE) |>
        filter(term == "workshop_Treatment:type_dummy") |>
        mutate(horizon = h, contrast = c_lab, outcome = Y)
    }))
  }))
}))
```

```{r}
#| label: fig-s4-format
#| fig-width: 12
#| fig-height: 5.5
#| fig-cap: "Fig. S5. Differential effects for emotional political videos."

fig_s4_type_treat_did <- est_did |>
  mutate(
    horizon = factor(horizon, levels = horizon_wave_levels),
    outcome = factor(outcome, levels = outcome_order_did),
    contrast = factor(contrast, levels = rev(names(contrast_specs))),
    super = outcome_super(outcome)
  ) |>
  ggplot(aes(x = estimate, y = contrast)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(horizon ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = shared_binary_x_scales(est_did, outcome_order_did)) +
  labs(
    x = "Treatment × type interaction",
    y = NULL,
    title = "Treatment effect on the emotional-minus-other gap",
    subtitle = "Pairwise samples; video FE; cluster-robust 95% CIs by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10),
    panel.spacing.y = unit(6, "pt")
  )

write_fig(
  stem = "fig_s4_type_treat_did",
  estimates = est_did,
  plot = fig_s4_type_treat_did,
  width = 12,
  height = 5.5,
  publish = si_pdf("fig_s4_type_treat_did")
)
```

## Tables S5–S8. Emotional vs other content-type contrasts

Wave 1 like and report: emotional vs politically neutral (Tables S5–S6) and emotional vs entertainment (Tables S7–S8). Video FE; cluster ID. Columns: ALL and sending parties.

```{r}
#| label: tab-s5-s8-analysis

compare_outcomes <- c("Like", "Report")
compare_group_names <- c("ALL", names(party_codes))

fit_type_contrast <- function(df, outcome_name, type_var) {
  y <- v_outcomes[[outcome_name]]
  feols(
    as.formula(paste0(y, " ~ workshop_Treatment * ", type_var, " | video")),
    data = df,
    cluster = ~ID
  )
}

type_contrast_coef_map <- list(
  "workshop_Treatment" = "Treatment (comparison type)",
  "workshop_Treatment:emotional" = "Treatment × type"
)

df_pol <- datasets$wave_9 |>
  filter(strategy_2 %in% strategies) |>
  mutate(emotional = as.integer(strategy_2 == strategies[1]))

models_emo_neu <- lapply(compare_outcomes, function(Y) {
  fits <- c(
    list(ALL = fit_type_contrast(df_pol, Y, "emotional")),
    lapply(names(party_codes), function(P) {
      fit_type_contrast(df_pol |> filter(party == P), Y, "emotional")
    }) |> setNames(names(party_codes))
  )
  fits[compare_group_names]
}) |>
  setNames(compare_outcomes)

df_ee <- datasets$wave_9 |>
  filter(strategy_2 %in% c(strategies[1], "entertainment")) |>
  mutate(emotional = as.integer(strategy_2 == strategies[1]))

models_emo_ent <- lapply(compare_outcomes, function(Y) {
  fits <- c(
    list(ALL = fit_type_contrast(df_ee, Y, "emotional")),
    lapply(names(party_codes), function(P) {
      df_p <- df_ee |> filter(party == P | strategy_2 == "entertainment")
      fit_type_contrast(df_p, Y, "emotional")
    }) |> setNames(names(party_codes))
  )
  fits[compare_group_names]
}) |>
  setNames(compare_outcomes)
```

```{r}
#| label: tab-s5-s8-format
#| results: 'asis'

write_type_contrast <- function(models, dest_stem, caption, label, html_caption = caption) {
  write_tab_rds(models, dest_stem)
  texreg::texreg(
    models,
    file = file.path(tab_dir, paste0(dest_stem, ".tex")),
    digits = 3,
    include.ci = FALSE,
    custom.model.names = names(models),
    custom.coef.map = type_contrast_coef_map,
    caption = caption,
    label = label,
    stars = texreg_stars
  )
  publish_tex(dest_stem)
  texreg::htmlreg(
    models,
    digits = 3,
    include.ci = FALSE,
    custom.model.names = names(models),
    custom.coef.map = type_contrast_coef_map,
    caption = html_caption,
    stars = texreg_stars
  )
}

write_type_contrast(
  models_emo_neu$Like,
  "tab_s5_emo_vs_neutral_like",
  "Emotional vs politically neutral: Like (Wave 1). Video FE; SEs clustered by respondent.",
  "tab:compare_emotional_vs_neutral_like",
  "Table S5. Emotional vs politically neutral: Like (short-term). Video FE; SEs clustered by respondent."
)
write_type_contrast(
  models_emo_neu$Report,
  "tab_s6_emo_vs_neutral_report",
  "Emotional vs politically neutral: Report (Wave 1). Video FE; SEs clustered by respondent.",
  "tab:compare_emotional_vs_neutral_report",
  "Table S6. Emotional vs politically neutral: Report (short-term). Video FE; SEs clustered by respondent."
)
write_type_contrast(
  models_emo_ent$Like,
  "tab_s7_emo_vs_ent_like",
  "Emotional vs entertainment: Like (Wave 1). Video FE; SEs clustered by respondent.",
  "tab:compare_emotional_vs_entertainment_like",
  "Table S7. Emotional vs entertainment: Like (short-term). Video FE; SEs clustered by respondent."
)
write_type_contrast(
  models_emo_ent$Report,
  "tab_s8_emo_vs_ent_report",
  "Emotional vs entertainment: Report (Wave 1). Video FE; SEs clustered by respondent.",
  "tab:compare_emotional_vs_entertainment_report",
  "Table S8. Emotional vs entertainment: Report (short-term). Video FE; SEs clustered by respondent."
)
```

## Fig. S6. Attrition (0/1) regressed on standardized pre-treatment covariates

Stem: `fig_s6_attrition_covariates`. Main-effect linear probability models.

```{r}
#| label: fig-s6-analysis
#| message: false
#| warning: false

covs <- names(labels_en)
names(covs) <- labels_en
stopifnot(n_distinct(df_w9_w10$id_w9) == nrow(df_w9_w10))

results_main <- lapply(covs, function(v) {
  as.formula(paste0("attrit ~ ", v)) |>
    lm_robust(data = df_w9_w10 |> mutate(across(all_of(v), scale))) |>
    tidy(conf.int = TRUE) |>
    filter(term == v)
}) |>
  bind_rows(.id = "label")
```

```{r}
#| label: fig-s6-format
#| fig-height: 12
#| fig-width: 9
#| fig-cap: "Fig. S6. Attrition (0/1) regressed on standardized pre-treatment covariates (main effects; linear probability models)."

fig_s6 <- results_main |>
  ggplot(aes(x = estimate, y = forcats::fct_reorder(label, estimate))) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0) +
  geom_point() +
  labs(
    title = "Covariate main effects on attrition (LPM)",
    x = "Covariate estimate (Δ probability of attrition)",
    y = NULL
  ) +
  theme_bw()

write_fig(
  stem = "fig_s6_attrition_covariates",
  estimates = results_main,
  plot = fig_s6,
  width = 7,
  height = 12,
  publish = si_pdf("fig_s6_attrition_covariates")
)
```

## Table S9. Attrition by treatment condition

```{r}
#| label: tab-s9-analysis

attrit_counts <- df_w9_w10 |>
  mutate(arm = ifelse(workshop == 1, "Treatment", "Control")) |>
  count(arm, attrit) |>
  tidyr::complete(arm, attrit = c(0, 1), fill = list(n = 0))

attrit_summary <- attrit_counts |>
  group_by(arm) |>
  summarise(
    original_n = sum(n),
    retained = sum(n[attrit == 0]),
    attrited = sum(n[attrit == 1]),
    .groups = "drop"
  ) |>
  mutate(rate = 100 * attrited / original_n)

attrit_test <- df_w9_w10 |>
  mutate(treat = as.integer(workshop == 1)) |>
  lm_robust(attrit ~ treat, data = _)
attrit_test_td <- tidy(attrit_test, conf.int = TRUE) |> filter(term == "treat")
```

```{r}
#| label: tab-s9-format
#| results: 'asis'

overall <- attrit_summary |>
  summarise(
    arm = "Overall",
    original_n = sum(original_n),
    retained = sum(retained),
    attrited = sum(attrited)
  ) |>
  mutate(rate = 100 * attrited / original_n)

attrit_rows <- bind_rows(
  attrit_summary |> arrange(arm != "Control", arm),
  overall
)
d <- attrit_test_td$estimate
p_attrit <- attrit_test_td$p.value
ci <- c(attrit_test_td$conf.low, attrit_test_td$conf.high)

fmt_row <- function(r) {
  sprintf(
    "%s & %s & %s & %s & %.2f \\\\",
    r$arm, r$original_n, r$retained, r$attrited, r$rate
  )
}
tex <- c(
  "\\begin{table}",
  "\\caption{\\label{tab:attrition-summary}Attrition by treatment condition.}",
  "\\centering",
  "\\begin{threeparttable}",
  "\\begin{tabular}[t]{lrrrr}",
  "\\toprule",
  "Condition & Original $N$ & Retained & Attrited & Attrition rate (\\%)\\\\",
  "\\midrule",
  vapply(seq_len(nrow(attrit_rows)), function(i) fmt_row(attrit_rows[i, ]), character(1)),
  "\\bottomrule",
  "\\end{tabular}",
  "\\begin{tablenotes}",
  sprintf(
    "\\item Note: The treatment--control difference is %.2f percentage points (95\\%% CI: %.2f to %.2f; $p=%.3f$).",
    100 * d, 100 * ci[1], 100 * ci[2], p_attrit
  ),
  "\\end{tablenotes}",
  "\\end{threeparttable}",
  "\\end{table}"
)
writeLines(tex, file.path(tab_dir, "tab_s9_attrition.tex"))
publish_tex("tab_s9_attrition")
knitr::kable(
  attrit_rows,
  digits = 2,
  caption = "Table S9. Attrition by treatment condition"
)
```

## Fig. S7. Attrition (0/1) regressed on the interaction between treatment and pre-treatment covariates

Stem: `fig_s7_attrition_interaction`.

```{r}
#| label: fig-s7-analysis
#| message: false
#| warning: false

results_int <- lapply(covs, function(v) {
  as.formula(paste0("attrit ~ workshop * ", v)) |>
    lm_robust(data = df_w9_w10 |> mutate(across(all_of(v), scale))) |>
    tidy(conf.int = TRUE) |>
    filter(grepl(":", term))
}) |>
  bind_rows(.id = "label")
```

```{r}
#| label: fig-s7-format
#| fig-height: 12
#| fig-width: 9
#| fig-cap: "Fig. S7. Attrition (0/1) regressed on the interaction between treatment and pre-treatment covariates."

fig_s7 <- results_int |>
  ggplot(aes(x = estimate, y = forcats::fct_reorder(label, estimate))) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0) +
  geom_point() +
  labs(
    title = "Treatment × covariate interactions on attrition (LPM)",
    x = "Interaction estimate (Δ probability of attrition)",
    y = NULL
  ) +
  theme_bw()

write_fig(
  stem = "fig_s7_attrition_interaction",
  estimates = results_int,
  plot = fig_s7,
  width = 7,
  height = 12,
  publish = si_pdf("fig_s7_attrition_interaction")
)
```

## Fig. S8. Short-term pooled engagement effects among non-attriters

Stem: `fig_s8_fig1_nonattriters`. Figure 1 Wave 1 companion, restricted to respondents retained in Wave 2. Same six outcomes and Engagement / Attention super-headers as Figure 1.

```{r}
#| label: fig-s8-analysis

s8_outcomes <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])
nonattrit_ids <- df_w9_w10 |>
  filter(attrit == 0) |>
  pull(id_w9) |>
  as.character()
df_w9_nonattrit <- datasets$wave_9 |>
  filter(as.character(ID) %in% nonattrit_ids)
estimates_s8 <- estimate_pooled_ates(df_w9_nonattrit, s8_outcomes) |>
  mutate(horizon = "Wave 1")
```

```{r}
#| label: fig-s8-format
#| fig-width: 12
#| fig-height: 3.5
#| fig-cap: "Fig. S8. Short-term pooled engagement effects (Like, Report, Share, Bookmark) by content strategy, restricted to non-attriters. Attrition-sensitivity check for manuscript Figure 1 showing results largely unchanged."

fig_s8 <- estimates_s8 |>
  mutate(
    horizon = factor(horizon, levels = horizon_wave_levels),
    strategy = factor(as.character(strategy), levels = rev(strategy_order_article)),
    outcome = factor(outcome, levels = s8_outcomes),
    super = outcome_super(outcome),
    strat_color = as.character(strategy)
  ) |>
  ggplot(aes(x = estimate, y = strategy, color = strat_color)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(horizon ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = shared_binary_x_scales(estimates_s8, s8_outcomes)) +
  scale_color_manual(values = strategy_color_values, guide = "none") +
  labs(
    x = "Average treatment effect",
    y = NULL,
    title = "Pooled Wave 1 treatment effects (non-attriters)",
    subtitle = "Video FE; SEs clustered by respondent; retained respondents only"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10),
    panel.spacing.y = unit(6, "pt")
  )

write_fig(
  stem = "fig_s8_fig1_nonattriters",
  estimates = estimates_s8,
  plot = fig_s8,
  width = 12,
  height = 3.5,
  publish = si_pdf("fig_s8_fig1_nonattriters")
)
```

## Fig. S9. Long-term treatment effects excluding repeated video exposure

Stem: `fig_s9_longterm_no_repeat`. Wave 2 ATEs after dropping respondent–video pairs already shown in both waves
(`shown_both_waves == 0`; flag merged in `1_data_prep.qmd`).
Super-columns: Engagement (first four) and Attention (skip, watch time).

```{r}
#| label: fig-s9-analysis

df_w10_norepeat <- df_w10_no_repeated_videos
cat(
  "Wave 10 rows: ", nrow(datasets$wave_10),
  "; after dropping repeats (shown_both_waves == 0): ", nrow(df_w10_norepeat),
  "; dropped: ", nrow(datasets$wave_10) - nrow(df_w10_norepeat), "\n",
  sep = ""
)
estimates_s9 <- bind_rows(
  estimate_pooled_ates(df_w10_norepeat, l_outcomegroups$main),
  estimate_pooled_ates(df_w10_norepeat, l_outcomegroups[["_other"]])
) |>
  mutate(horizon = "Wave 2")
```

```{r}
#| label: fig-s9-format
#| fig-width: 12
#| fig-height: 3.5
#| fig-cap: "Fig. S9. Long-term treatment effects excluding repeated video exposure."

fig_s9 <- estimates_s9 |>
  mutate(
    strategy = factor(as.character(strategy), levels = rev(strategy_order_article)),
    outcome = factor(
      outcome,
      levels = c(l_outcomegroups$main, l_outcomegroups[["_other"]])
    ),
    super = outcome_super(outcome),
    strat_color = as.character(strategy)
  ) |>
  ggplot(aes(x = estimate, y = strategy, color = strat_color)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(. ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(
    x = shared_binary_x_scales(
      estimates_s9,
      c(l_outcomegroups$main, l_outcomegroups[["_other"]])
    )
  ) +
  scale_color_manual(values = strategy_color_values, guide = "none") +
  labs(
    x = "Average treatment effect",
    y = NULL,
    title = "Wave 2 effects excluding repeated video exposure",
    subtitle = "Video FE; SEs clustered by respondent"
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10)
  )

write_fig(
  stem = "fig_s9_longterm_no_repeat",
  estimates = estimates_s9,
  plot = fig_s9,
  width = 12,
  height = 3.5,
  publish = si_pdf("fig_s9_longterm_no_repeat")
)
```

## Tables S10–S11. AfD-specific triple interactions

```{r}
#| label: tab-s10-s11-analysis

afd_3way_outcomes <- c("Like", "Share", "Bookmark", "Report")
afd_3way_coef_map <- list(
  "treatment_demeaned" = "Treatment (demeaned)",
  "AFD_supporter_demeaned" = "AfD supporter (demeaned)",
  "treatment_demeaned:AFD_supporter_demeaned" = "Treatment × AfD supporter (demeaned)",
  "treatment_demeaned:AFD_videos_demeaned" = "Treatment × AfD video (demeaned)",
  "AFD_supporter_demeaned:AFD_videos_demeaned" = "AfD supporter × AfD video (demeaned)",
  "treatment_demeaned:AFD_supporter_demeaned:AFD_videos_demeaned" =
    "Treatment × AfD supporter × AfD video (demeaned)"
)

prep_afd_3way <- function(df) {
  df |>
    filter(strategy_2 == strategies[1]) |>
    mutate(
      AFD_supporter = as.integer(party_preference_afd == 1),
      AFD_videos = as.integer(party == "AfD")
    ) |>
    mutate(
      treatment_demeaned = workshop_Treatment - mean(workshop_Treatment, na.rm = TRUE),
      AFD_supporter_demeaned = AFD_supporter - mean(AFD_supporter, na.rm = TRUE),
      AFD_videos_demeaned = AFD_videos - mean(AFD_videos, na.rm = TRUE)
    )
}

fit_afd_3way <- function(df, outcome_name) {
  feols(
    as.formula(paste0(
      v_outcomes[[outcome_name]],
      " ~ treatment_demeaned * AFD_supporter_demeaned * AFD_videos_demeaned | video"
    )),
    data = df,
    cluster = ~ID
  )
}

df_afd_3way <- prep_afd_3way(datasets$wave_9)
df_afd_3way_lt <- prep_afd_3way(datasets$wave_10)
models_afd_3way <- lapply(afd_3way_outcomes, function(Y) fit_afd_3way(df_afd_3way, Y)) |>
  setNames(afd_3way_outcomes)
models_afd_3way_lt <- lapply(afd_3way_outcomes, function(Y) fit_afd_3way(df_afd_3way_lt, Y)) |>
  setNames(afd_3way_outcomes)
```

```{r}
#| label: tab-s10-s11-format
#| results: 'asis'

write_afd_3way <- function(models, dest_stem, caption, label, html_caption = caption) {
  write_tab_rds(models, dest_stem)
  texreg::texreg(
    models,
    file = file.path(tab_dir, paste0(dest_stem, ".tex")),
    digits = 3,
    include.ci = FALSE,
    custom.model.names = afd_3way_outcomes,
    custom.coef.map = afd_3way_coef_map,
    caption = caption,
    label = label,
    stars = texreg_stars
  )
  publish_tex(dest_stem)
  texreg::htmlreg(
    models,
    digits = 3,
    include.ci = FALSE,
    custom.model.names = afd_3way_outcomes,
    custom.coef.map = afd_3way_coef_map,
    caption = html_caption,
    stars = texreg_stars
  )
}

write_afd_3way(
  models_afd_3way,
  "tab_s10_afd_3way_short",
  "Treatment × AfD supporter × AfD video (all demeaned): Like/Share/Bookmark/Report (emotional political videos, Wave 1). Video FE; SEs clustered by respondent.",
  "tab:afd_video_3way_demeaned",
  "Table S10. Treatment × AfD supporter × AfD video (all demeaned): Like/Share/Bookmark/Report (emotional political videos, short-term). Video FE; SEs clustered by respondent."
)
write_afd_3way(
  models_afd_3way_lt,
  "tab_s11_afd_3way_long",
  "Treatment × AfD supporter × AfD video (all demeaned): Like/Share/Bookmark/Report (emotional political videos, Wave 2). Video FE; SEs clustered by respondent.",
  "tab:afd_video_3way_demeaned_longterm",
  "Table S11. Treatment × AfD supporter × AfD video (all demeaned): Like/Share/Bookmark/Report (emotional political videos, long-term / wave 10). Video FE; SEs clustered by respondent."
)
```

## Table S12. Effect of digital literacy workshop on AfD identification

```{r}
#| label: tab-s12-analysis

df_w9_w10 <- df_w9_w10 |>
  mutate(
    party_id_w9_afd_demeaned = party_id_w9_afd - mean(party_id_w9_afd, na.rm = TRUE)
  )
models_s12 <- list(
  identification = lm_robust(
    party_id_w10_afd ~ workshop * party_id_w9_afd_demeaned,
    data = df_w9_w10
  ),
  conditional_afd = lm_robust(
    party_id_w10_afd ~ workshop,
    data = df_w9_w10 |> filter(party_id_w9_afd == 1)
  ),
  conditional_non_afd = lm_robust(
    party_id_w10_afd ~ workshop,
    data = df_w9_w10 |> filter(party_id_w9_afd == 0)
  )
)
```

```{r}
#| label: tab-s12-format
#| results: 'asis'

texreg::texreg(
  models_s12,
  file = file.path(tab_dir, "tab_s12_afd_identification.tex"),
  digits = 3,
  include.ci = FALSE,
  custom.model.names = c("All respondents", "AfD identifiers", "Non-AfD respondents"),
  custom.coef.map = list(
    "(Intercept)" = "Intercept",
    "workshop" = "Treatment (workshop)",
    "party_id_w9_afd_demeaned" = "AfD ID (Wave 1, demeaned)",
    "workshop:party_id_w9_afd_demeaned" = "Treatment × AfD ID (demeaned)"
  ),
  caption = "Effect of digital literacy workshop on AfD identification (Wave 2).",
  label = "tab:afd_maintained_support",
  stars = texreg_stars
)
publish_tex("tab_s12_afd_identification")
texreg::htmlreg(
  models_s12,
  digits = 3,
  include.ci = FALSE,
  custom.model.names = c("All respondents", "AfD identifiers", "Non-AfD respondents"),
  caption = "Table S12. Effect of digital literacy workshop on AfD identification (wave 10).",
  stars = texreg_stars
)
```

## Fig. S10. Effect on party identification conditional on prior identification

Stem: `fig_s10_pid_by_prior`.

```{r}
#| label: fig-s10-analysis
#| fig-height: 7
#| fig-width: 7

maintained_results <- party_codes |>
  lapply(function(party) {
    w9 <- paste0("party_id_w9_", party)
    w10 <- paste0("party_id_w10_", party)
    df_tmp <- df_w9_w10 |>
      mutate(
        id_w9 = .data[[w9]],
        id_w9_demeaned = id_w9 - mean(id_w9, na.rm = TRUE),
        id_w10 = .data[[w10]]
      )
    m_all <- lm_robust(id_w10 ~ workshop * id_w9_demeaned, data = df_tmp)
    m_id <- lm_robust(id_w10 ~ workshop, data = df_tmp |> filter(id_w9 == 1))
    m_non <- lm_robust(id_w10 ~ workshop, data = df_tmp |> filter(id_w9 == 0))
    bind_rows(
      tidy(m_all) |> filter(term == "workshop") |> mutate(group = "All respondents"),
      tidy(m_id) |> filter(term == "workshop") |> mutate(group = "Identifiers"),
      tidy(m_non) |> filter(term == "workshop") |> mutate(group = "Non-identifiers")
    ) |>
      mutate(party = party_names[[party]])
  }) |>
  bind_rows()

party_order_maintained <- maintained_results |>
  filter(group == "All respondents") |>
  arrange(estimate) |>
  pull(party)
maintained_results <- maintained_results |>
  mutate(
    party = factor(party, levels = party_order_maintained),
    group = factor(group, levels = c("All respondents", "Identifiers", "Non-identifiers"))
  )
```

```{r}
#| label: fig-s10-format
#| fig-height: 9
#| fig-width: 7
#| fig-cap: "Fig. S10. Effect on party identification conditional on prior identification."

fig_s10 <- maintained_results |>
  ggplot(aes(x = estimate, y = party, color = group)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_point(position = position_dodge(width = 0.6), size = 2.5) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.6),
    height = 0.2
  ) +
  geom_text(
    aes(label = sprintf("%.3f (p = %.3f)", estimate, p.value), group = group),
    position = position_dodge(width = 0.6),
    hjust = 0.5, vjust = -0.7, size = 2.5, show.legend = FALSE
  ) +
  labs(
    x = "Effect of workshop on party identification (Wave 2)",
    y = "Party",
    color = NULL,
    title = "Effects of digital literacy workshop on party identification"
  ) +
  theme_bw()

write_fig(
  stem = "fig_s10_pid_by_prior",
  estimates = maintained_results,
  plot = fig_s10,
  width = 7,
  height = 9,
  publish = si_pdf("fig_s10_pid_by_prior")
)
```

## Fig. S11. Change in party identification, wave 1 to wave 2, full sample

Stem: `fig_s11_pid_transitions`. Figs. S12–S13 use the same transition construction for treatment and control.

```{r}
#| label: fig-s11-analysis

build_pid_lodes <- function(df_input) {
  labs <- party_names
  from <- df_input |>
    select(id_w9, starts_with("party_id_w9")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      from_party = recode(sub("^party_id_w9_(.*)$", "\\1", var), !!!labs)
    )
  to <- df_input |>
    select(id_w9, starts_with("party_id_w10")) |>
    pivot_longer(-id_w9, names_to = "var", values_to = "val") |>
    filter(val == 1) |>
    transmute(
      id_w9,
      to_party = recode(sub("^party_id_w10_(.*)$", "\\1", var), !!!labs)
    )
  transitions <- inner_join(from, to, by = "id_w9") |>
    count(`Wave 1` = from_party, `Wave 2` = to_party, name = "Freq")
  totN <- sum(transitions$Freq)
  share_w9 <- transitions |>
    group_by(`Wave 1`) |>
    summarise(s9 = sum(Freq) / totN, .groups = "drop")
  share_w10 <- transitions |>
    group_by(`Wave 2`) |>
    summarise(s10 = sum(Freq) / totN, .groups = "drop")
  net_pp <- share_w10 |>
    left_join(share_w9, by = c("Wave 2" = "Wave 1")) |>
    mutate(
      delta_pp = (s10 - s9) * 100,
      label_right = sprintf("%s\n(%+0.2f pp)", `Wave 2`, delta_pp)
    ) |>
    select(`Wave 2`, label_right)
  lodes <- transitions |>
    mutate(Share = Freq / totN) |>
    to_lodes_form(axes = 1:2, id = "alluvium") |>
    mutate(
      x = factor(x, levels = c("Wave 1", "Wave 2")),
      stratum_lab = ifelse(
        x == "Wave 2",
        net_pp$label_right[match(stratum, net_pp$`Wave 2`)],
        as.character(stratum)
      )
    )
  party_cols <- c(
    "CDU/CSU" = "#000000",
    "SPD" = "#E3000F",
    "Grüne" = "#0DB02B",
    "FDP" = "#FFED00",
    "Linke" = "#E2382A",
    "AfD" = "#009EE0",
    "BSW" = "#18A19A"
  )
  list(lodes = lodes, party_cols = party_cols)
}

plot_pid_alluvial <- function(lodes, party_cols, title_text) {
  ggplot(
    lodes,
    aes(x = x, stratum = stratum, alluvium = alluvium, y = Share, fill = stratum, label = stratum_lab)
  ) +
    geom_alluvium(alpha = 0.7, color = NA, knot.pos = 0.4) +
    geom_stratum(fill = "white", color = "black", size = 0.3) +
    geom_text(stat = "stratum", size = 4) +
    scale_fill_manual(values = party_cols, guide = "none") +
    scale_x_discrete(labels = c("Wave 1", "Wave 2"), expand = c(0.05, 0.05)) +
    labs(x = NULL, y = NULL, title = title_text) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      panel.grid = element_blank(),
      axis.text.y = element_blank()
    )
}

pid_overall <- build_pid_lodes(df_w9_w10)
```

```{r}
#| label: fig-s11-format
#| fig-cap: "Fig. S11. Change in party identification, wave 1 to wave 2, full sample."
fig_s11 <- plot_pid_alluvial(
  pid_overall$lodes, pid_overall$party_cols,
  "Party identification transitions: Wave 1 \u2192 Wave 2"
)
write_fig(
  stem = "fig_s11_pid_transitions",
  estimates = pid_overall,
  plot = fig_s11,
  publish = si_pdf("fig_s11_pid_transitions")
)
```

```{r}
#| label: fig-s12-analysis
pid_treat <- build_pid_lodes(df_w9_w10 |> filter(workshop == 1))
```

## Fig. S12. Change in party identification, wave 1 to wave 2, treatment group

Stem: `fig_s12_pid_transitions_treat`.

```{r}
#| label: fig-s12-format
#| fig-cap: "Fig. S12. Change in party identification, wave 1 to wave 2, treatment group."
fig_s12 <- plot_pid_alluvial(
  pid_treat$lodes, pid_treat$party_cols,
  "Party identification transitions (treatment)"
)
write_fig(
  stem = "fig_s12_pid_transitions_treat",
  estimates = pid_treat,
  plot = fig_s12,
  publish = si_pdf("fig_s12_pid_transitions_treat")
)
```

```{r}
#| label: fig-s13-analysis
pid_control <- build_pid_lodes(df_w9_w10 |> filter(workshop == 0))
```

## Fig. S13. Change in party identification, wave 1 to wave 2, control group

Stem: `fig_s13_pid_transitions_control`.

```{r}
#| label: fig-s13-format
#| fig-cap: "Fig. S13. Change in party identification, wave 1 to wave 2, control group."
fig_s13 <- plot_pid_alluvial(
  pid_control$lodes, pid_control$party_cols,
  "Party identification transitions (control)"
)
write_fig(
  stem = "fig_s13_pid_transitions_control",
  estimates = pid_control,
  plot = fig_s13,
  publish = si_pdf("fig_s13_pid_transitions_control")
)
```

## Fig. S14. Effects of the digital literacy workshop on propensity to vote (PTV)

Stem: `fig_s14_ptv`. By party and prior identification.

```{r}
#| label: fig-s14-analysis

estimate_ptv_by_id <- function(post_prefix) {
  party_codes |>
    lapply(function(party) {
      pre_var <- paste0("ptv_w9_pre_", party)
      post_var <- paste0(post_prefix, party)
      id_var <- paste0("party_id_w9_", party)
      fml <- as.formula(paste0(post_var, " ~ workshop * ", pre_var))
      m_all <- lm_robust(fml, data = df_w9_w10)
      m_id <- lm_robust(fml, data = df_w9_w10 |> filter(.data[[id_var]] == 1))
      m_non <- lm_robust(fml, data = df_w9_w10 |> filter(.data[[id_var]] == 0))
      bind_rows(
        tidy(m_all) |> filter(term == "workshop") |> mutate(group = "All respondents"),
        tidy(m_id) |> filter(term == "workshop") |> mutate(group = "Identifiers"),
        tidy(m_non) |> filter(term == "workshop") |> mutate(group = "Non-identifiers")
      ) |>
        mutate(party = party_names[[party]])
    }) |>
    bind_rows()
}

ptv_short <- estimate_ptv_by_id("ptv_w9_post_")
ptv_long <- estimate_ptv_by_id("ptv_w10_")
group_levels <- c("All respondents", "Identifiers", "Non-identifiers")
party_order_ptv <- ptv_short |>
  filter(group == "All respondents") |>
  arrange(estimate) |>
  pull(party) |>
  as.character()
estimates_ptv <- bind_rows(
  ptv_short |> mutate(horizon = "Wave 1"),
  ptv_long |> mutate(horizon = "Wave 2")
) |>
  mutate(
    horizon = factor(horizon, levels = horizon_wave_levels),
    party = factor(as.character(party), levels = party_order_ptv),
    group = factor(as.character(group), levels = group_levels)
  )
```

```{r}
#| label: fig-s14-format
#| fig-width: 10
#| fig-height: 8
#| fig-cap: "Fig. S14. Effects of the digital literacy workshop on propensity to vote (PTV), by party and prior identification."

dodge_ptv <- position_dodge(width = 0.6)
fig_s14 <- estimates_ptv |>
  ggplot(aes(x = estimate, y = party, color = group)) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_point(position = dodge_ptv, size = 2.5) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    position = dodge_ptv,
    height = 0.2
  ) +
  geom_text(
    aes(label = sprintf("%.3f (p = %.3f)", estimate, p.value), group = group),
    position = dodge_ptv, hjust = 0.5, vjust = -0.7, size = 2.2, show.legend = FALSE
  ) +
  facet_grid(cols = vars(horizon)) +
  labs(
    x = "Effect of workshop on PTV (0–1 scale)",
    y = "Party",
    color = NULL,
    title = "PTV effects of digital literacy workshop"
  ) +
  theme_bw(base_size = 11) +
  theme(
    legend.position = "bottom",
    strip.background = element_rect(fill = "grey95", color = "grey80")
  )

write_fig(
  stem = "fig_s14_ptv",
  estimates = estimates_ptv,
  plot = fig_s14,
  width = 10,
  height = 8,
  publish = si_pdf("fig_s14_ptv")
)
```

## Table S13. PAP H1a reconciliation

```{r}
#| label: tab-s13-analysis

df_h1_emo <- datasets$wave_9 |>
  filter(strategy_2 == strategies[1]) |>
  mutate(
    engage = rowMeans(cbind(videoSharep1r, videoLikep1r, videoBookmarkp1r), na.rm = FALSE)
  )
h1_outcomes <- c(
  Like = v_outcomes[["Like"]],
  Share = v_outcomes[["Share"]],
  Bookmark = v_outcomes[["Bookmark"]],
  Engage = "engage"
)
models_h1 <- lapply(h1_outcomes, function(y) {
  feols(as.formula(paste0(y, " ~ workshop_Treatment | video")), data = df_h1_emo, cluster = ~ID)
})
h1_comp <- c("Like", "Share", "Bookmark")
p_h1_raw <- sapply(models_h1[h1_comp], \(m) coeftable(m)["workshop_Treatment", "Pr(>|t|)"])
p_h1_bh <- p.adjust(p_h1_raw, method = "BH")
h1_bh_row <- c(sprintf("%.3f", p_h1_bh[h1_comp]), "---")
names(h1_bh_row) <- names(models_h1)
```

```{r}
#| label: tab-s13-format
#| results: 'asis'

h1_caption <- paste(
  "PAP H1a reconciliation: Like, Share, Bookmark, and engage = mean(share, like, bookmark)",
  "on emotional political videos (Wave 1). Video FE; SEs clustered by respondent.",
  "Row p (BH FDR): Benjamini--Hochberg FDR correction across the three component tests",
  "(Like, Share, Bookmark); Engage is not in that family."
)
texreg::texreg(
  models_h1,
  file = file.path(tab_dir, "tab_s13_pap_h1a.tex"),
  digits = 3,
  include.ci = FALSE,
  custom.model.names = names(models_h1),
  custom.coef.map = list("workshop_Treatment" = "Treatment"),
  custom.gof.rows = list("p (BH FDR)" = unname(h1_bh_row)),
  caption = h1_caption,
  label = "tab:pap_h1a_engage_emotional",
  stars = texreg_stars
)
publish_tex("tab_s13_pap_h1a")
texreg::htmlreg(
  models_h1,
  digits = 3,
  include.ci = FALSE,
  custom.model.names = names(models_h1),
  custom.coef.map = list("workshop_Treatment" = "Treatment"),
  custom.gof.rows = list("p (BH FDR)" = unname(h1_bh_row)),
  caption = paste("Table S13.", h1_caption),
  stars = texreg_stars
)
```

## Table S14. Pairwise outcome correlations

Pairwise outcome correlations on emotionally manipulative political videos, Wave 1. Cells expanded to three rows ($r_T$, $r_C$, $\Delta$) with a rule after each outcome group. Compiled SI Table S15 (PAP reconciliation) is written in the SI `.tex`, not here.

```{r}
#| label: tab-s14-analysis

oc_labs <- c("Like", "Share", "Bookmark", "Report", "Watch time", "Skip")
oc_vars <- c(
  Like = "videoLikep1r",
  Share = "videoSharep1r",
  Bookmark = "videoBookmarkp1r",
  Report = "videoCommentTickedp1r",
  `Watch time` = "watch_percentage_",
  Skip = "skipped_video_"
)
star_p <- function(p) {
  if (!is.finite(p)) return("")
  if (p < 0.01) return("***")
  if (p < 0.05) return("**")
  if (p < 0.10) return("*")
  ""
}
fmt_r <- function(x) {
  if (!is.finite(x)) return("")
  sprintf("%0.2f", x)
}
pair_cor <- function(x, y) {
  ok <- is.finite(x) & is.finite(y)
  n <- sum(ok)
  if (n < 3) return(list(r = NA_real_, n = n))
  list(r = suppressWarnings(cor(x[ok], y[ok])), n = n)
}
cluster_cor_diff_p <- function(yi, yj, mod, id) {
  ok <- is.finite(yi) & is.finite(yj) & is.finite(mod) & !is.na(id)
  if (sum(ok) < 8L) return(NA_real_)
  mod_ok <- as.numeric(mod[ok])
  if (length(unique(mod_ok)) < 2L) return(NA_real_)
  yi_ok <- as.numeric(yi[ok])
  yj_ok <- as.numeric(yj[ok])
  s_i <- stats::sd(yi_ok)
  s_j <- stats::sd(yj_ok)
  if (!is.finite(s_i) || !is.finite(s_j) || s_i <= 0 || s_j <= 0) return(NA_real_)
  d <- data.frame(
    yi_z = as.numeric(scale(yi_ok)),
    yj_z = as.numeric(scale(yj_ok)),
    mod = mod_ok,
    ID = as.character(id[ok]),
    stringsAsFactors = FALSE
  )
  fit <- tryCatch(feols(yi_z ~ yj_z * mod, data = d, cluster = ~ID), error = function(e) NULL)
  if (is.null(fit)) return(NA_real_)
  td <- broom::tidy(fit)
  hit <- td$term[grepl(":", td$term, fixed = TRUE)]
  if (length(hit) != 1L) return(NA_real_)
  as.numeric(td$p.value[td$term == hit])
}
oc_num <- function(x) {
  if (inherits(x, "haven_labelled")) x <- haven::zap_labels(x)
  as.numeric(x)
}
df_oc_tc <- datasets$wave_9 |>
  filter(strategy_2 == strategies[1]) |>
  transmute(
    ID = as.character(ID),
    mod_treat = as.integer(workshop_Treatment),
    across(all_of(unname(oc_vars)), oc_num)
  ) |>
  rename(!!!setNames(unname(oc_vars), oc_labs))

cells_tc <- {
  dat_a <- df_oc_tc[df_oc_tc$mod_treat == 1, , drop = FALSE]
  dat_b <- df_oc_tc[df_oc_tc$mod_treat == 0, , drop = FALSE]
  out <- vector("list", length(oc_labs) * length(oc_labs))
  k <- 0L
  for (i in seq_along(oc_labs)) {
    for (j in seq_along(oc_labs)) {
      k <- k + 1L
      rn <- oc_labs[i]
      cn <- oc_labs[j]
      if (identical(rn, cn)) {
        out[[k]] <- tibble(row = rn, col = cn, r_a = NA_real_, r_b = NA_real_,
                           delta = NA_real_, p = NA_real_, blank = TRUE)
        next
      }
      pa <- pair_cor(dat_a[[rn]], dat_a[[cn]])
      pb <- pair_cor(dat_b[[rn]], dat_b[[cn]])
      p <- cluster_cor_diff_p(df_oc_tc[[rn]], df_oc_tc[[cn]], df_oc_tc$mod_treat, df_oc_tc$ID)
      out[[k]] <- tibble(
        row = rn, col = cn, r_a = pa$r, r_b = pb$r, delta = pa$r - pb$r, p = p, blank = FALSE
      )
    }
  }
  bind_rows(out)
}
```

```{r}
#| label: tab-s14-format
#| results: 'asis'

star_tex <- function(p) {
  s <- star_p(p)
  if (!nzchar(s)) return("")
  paste0("^{", s, "}")
}
val_tex <- function(x, p = NA, blank = FALSE) {
  if (isTRUE(blank) || !is.finite(x)) return("")
  paste0(fmt_r(x), star_tex(p))
}
align <- paste0("ll", paste(rep("c", length(oc_labs)), collapse = ""))
header <- paste(c("Outcome", "", oc_labs), collapse = " & ")
body <- character(0)
html_mat <- matrix("", nrow = 3 * length(oc_labs), ncol = 2 + length(oc_labs))
colnames(html_mat) <- c("Outcome", "Stat", oc_labs)
html_i <- 0L
for (i in seq_along(oc_labs)) {
  rn <- oc_labs[i]
  row_t <- row_c <- row_d <- character(length(oc_labs))
  for (j in seq_along(oc_labs)) {
    cell <- cells_tc |> filter(row == rn, col == oc_labs[j])
    row_t[j] <- val_tex(cell$r_a, blank = cell$blank)
    row_c[j] <- val_tex(cell$r_b, blank = cell$blank)
    row_d[j] <- val_tex(cell$delta, cell$p, blank = cell$blank)
  }
  body <- c(
    body,
    paste(c(rn, "$r_{T}$", row_t), collapse = " & "),
    paste(c("", "$r_{C}$", row_c), collapse = " & "),
    paste0("\\rowcolor{ocrow} ", paste(c("", "$\\Delta$", row_d), collapse = " & "))
  )
  html_mat[html_i <- html_i + 1L, ] <- c(rn, "r_T", row_t)
  html_mat[html_i <- html_i + 1L, ] <- c("", "r_C", row_c)
  html_mat[html_i <- html_i + 1L, ] <- c("", "Delta", gsub("\\^\\{([^}]+)\\}", "*\\1", row_d, perl = TRUE))
}
note <- paste0(
  "\\multicolumn{", 2 + length(oc_labs), "}{l}{\\scriptsize{",
  "$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.10$ (clustered interaction: standardized $Y_i \\sim Y_j \\times$ group, cluster ID). Pairwise-complete $n$.",
  "}}"
)
body_grouped <- character(0)
for (g in seq_along(oc_labs)) {
  i0 <- (g - 1L) * 3L
  body_grouped <- c(
    body_grouped,
    paste0(body[i0 + 1L], " \\\\"),
    paste0(body[i0 + 2L], " \\\\"),
    paste0(body[i0 + 3L], " \\\\"),
    if (g < length(oc_labs)) "\\hline" else NULL
  )
}
tex <- c(
  "\\begin{table}",
  "\\begin{center}",
  "\\setlength{\\tabcolsep}{4pt}",
  paste0("\\begin{tabular}{", align, "}"),
  "\\hline",
  paste0(header, " \\\\"),
  "\\hline",
  body_grouped,
  "\\hline",
  paste0(note, " \\\\"),
  "\\end{tabular}",
  paste0(
    "\\caption{Pairwise outcome correlations (emotionally manipulative political videos; ",
    "video--respondent rows, Wave 1 only). ",
    "Within each outcome, three rows report $r_{T}$, $r_{C}$, and $\\Delta=r_{T}-r_{C}$ ",
    "with clustered-interaction stars ($*/**/***$) on $\\Delta$. Diagonal blank.}"
  ),
  "\\label{tab:outcome_cors_treat_ctrl}",
  "\\end{center}",
  "\\end{table}"
)
writeLines(tex, file.path(tab_dir, "tab_s14_outcome_cors.tex"))
publish_tex("tab_s14_outcome_cors")
knitr::kable(
  html_mat,
  caption = "Table S14. Pairwise outcome correlations (emotionally manipulative political videos; video-respondent rows, Wave 1). Groups of three rows: r_T, r_C, Delta.",
  align = c("l", "l", rep("c", length(oc_labs))),
  escape = FALSE,
  row.names = FALSE
)
```

## Fig. S15. Main engagement patterns without video fixed effects

Stem: `fig_s16_fig1_nofe` (filename retained; compiled SI number is S15 because the former ellipses figure is commented out of the SI TeX). Figure 1 companion without video fixed effects (cluster ID retained). Six outcomes with Engagement | Attention super-headers, as in Figure 1.

```{r}
#| label: fig-s16-analysis

s16_outcomes <- c(l_outcomegroups$main, l_outcomegroups[["_other"]])

estimates_s16 <- lapply(c("wave_9", "wave_10"), function(D) {
  df <- datasets[[D]]
  lapply(s16_outcomes, function(Y) {
    lapply(unique(as.character(df$strategy_2)), function(S) {
      feols(
        as.formula(paste(v_outcomes[[Y]], "~ workshop_Treatment")),
        data = df |> filter(strategy_2 == S),
        cluster = ~ID
      ) |>
        tidy(conf.int = TRUE) |>
        filter(term == "workshop_Treatment") |>
        mutate(
          outcome = Y,
          strategy = S,
          horizon = if (D == "wave_9") "Wave 1" else "Wave 2"
        )
    }) |> bind_rows()
  }) |> bind_rows()
}) |>
  bind_rows()
```

```{r}
#| label: fig-s16-format
#| fig-width: 12
#| fig-height: 5
#| fig-cap: "Fig. S15. Main engagement patterns without video fixed effects (respondent-clustered standard errors retained). Companion to the manuscript Figure 1 specification."

fig_s16 <- estimates_s16 |>
  mutate(
    horizon = factor(horizon, levels = horizon_wave_levels),
    strategy = factor(as.character(strategy), levels = rev(strategy_order_article)),
    outcome = factor(outcome, levels = s16_outcomes),
    super = outcome_super(outcome),
    strat_color = as.character(strategy)
  ) |>
  ggplot(aes(x = estimate, y = strategy, color = strat_color)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  geom_point(size = 1.8) +
  facet_nested(horizon ~ super + outcome, scales = "free_x") +
  facetted_pos_scales(x = shared_binary_x_scales(estimates_s16, s16_outcomes)) +
  scale_color_manual(values = strategy_color_values, guide = "none") +
  labs(
    x = "Average treatment effect",
    y = NULL,
    title = "PAP reconciliation: pooled effects without video FE",
    subtitle = "Cluster ID only (no video FE). Compare to primary Figure 1."
  ) +
  theme_bw(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, size = 9),
    axis.text.y = element_text(size = 9),
    strip.text = element_text(size = 10),
    panel.spacing.y = unit(6, "pt")
  )

write_fig(
  stem = "fig_s16_fig1_nofe",
  estimates = estimates_s16,
  plot = fig_s16,
  width = 12,
  height = 5,
  publish = si_pdf("fig_s16_fig1_nofe")
)
```

